---
title: "SNA Edge Betwenness fuull_no_zero_fancy"
author: "Leonardo Martins"
date: "17 de julho de 2016"
output: 
  html_document: 
    fig_caption: yes
    fig_height: 12
    fig_width: 12
    keep_md: yes
    number_sections: yes
    theme: flatly
    toc: yes
---
SNA Descritive Analysis from "Projeto Redes de Atenção às pessoas que consomem álcool e outras Drogas em Juiz de Fora-MG   Brazil"  - SNArRDJF

Here you can find a basic script to analysis data from SNArRDJF - this script was elaborated considering its use for orther matrix adjacency data from SNArRDJF - Here we are going to analyse:

# fuull_no_zero_fancy

`#########################
`# Basic Preparation #####
`#########################

#Loading objects generated with previous script 
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
rm(list = ls()) # removing previous objects to be sure that we don't have objects conflicts name
load("~/SNArRDJF/Robject/10_distance_paths_full_no_zero.RData")
```
##Reload packages
```{r, message=TRUE, warning=TRUE}
suppressMessages(library(RColorBrewer))
suppressMessages(library(car))
suppressMessages(library(xtable))
suppressMessages(library(igraph))
suppressMessages(library(miniCRAN))
suppressMessages(library(magrittr))
suppressMessages(library(keyplayer))
suppressMessages(library(dplyr))
suppressMessages(library(feather))
suppressMessages(library(visNetwork))
suppressMessages(library(knitr))
suppressMessages(library(DT))
```
##Adding phantom tools
```{r, message=TRUE, warning=TRUE}
#In order to get dinamic javascript object install those ones. If you get problems installing go to Stackoverflow.com and type your error to discover what to do. In some cases the libraries need to be intalled in outside R libs.
#devtools::install_github("wch/webshot")
#webshot::install_phantomjs()
```
##Setting a random seed - this is a good strategy to keep the same graph pattern layout in a new report generation
```{r, message=TRUE, warning=TRUE}
set.seed(123)
```

##Simplify Graph - removing loops and duble edges 
```{r, echo=T, message=FALSE, warning=FALSE}
full_no_zero<-simplify(full_no_zero) #Simplify
```

#Edges Newman-Girvan Edge-Betweenness
Edge betweenness Edge betweenness is equal to the number of shortest paths σst(e) from all vertices to all others that pass through that edge e
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
#Edge Betweenness
E(full_no_zero)$edge.btweenness<-edge.betweenness(full_no_zero, weights =E(full_no_zero)$weight)
full_no_zero_edge.betweenness <-edge.betweenness(full_no_zero, weights =E(full_no_zero)$weight)
```
#Edge Betweenness Descriptive
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
summary(full_no_zero_edge.betweenness)
sd(full_no_zero_edge.betweenness)
```
##Edge Betweenness Table
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
labels<-attr(E(full_no_zero), "vnames")
edgebt<-cbind(round(full_no_zero_edge.betweenness,2),labels)
datatable(edgebt)
```

#Saving objects with new variables and changes
```{r, echo=T, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
save.image("~/SNArRDJF/Robject/11_ebetweenness_full_no_zero.RData") 
```

