---
title: "SNA Diameter fuull_no_zero_fancy"
author: "Leonardo Martins"
date: "17 de julho de 2016"
output: 
  html_document: 
    fig_caption: yes
    fig_height: 12
    fig_width: 12
    keep_md: yes
    number_sections: yes
    theme: flatly
    toc: yes
---
SNA Descritive Analysis from "Projeto Redes de Atenção às pessoas que consomem álcool e outras Drogas em Juiz de Fora-MG   Brazil"  - SNArRDJF

Here you can find a basic script to analysis data from SNArRDJF - this script was elaborated considering its use for orther matrix adjacency data from SNArRDJF - Here we are going to analyse:

# fuull_no_zero_fancy

`#########################
`# Basic Preparation #####
`#########################

#Loading objects generated with previous script 
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
rm(list = ls()) # removing previous objects to be sure that we don't have objects conflicts name
load("~/SNArRDJF/Robject/14_kcore_full_no_zero.RData")
```
##Reload packages
```{r, message=TRUE, warning=TRUE}
suppressMessages(library(RColorBrewer))
suppressMessages(library(car))
suppressMessages(library(xtable))
suppressMessages(library(igraph))
suppressMessages(library(miniCRAN))
suppressMessages(library(magrittr))
suppressMessages(library(keyplayer))
suppressMessages(library(dplyr))
suppressMessages(library(feather))
suppressMessages(library(visNetwork))
suppressMessages(library(knitr))
suppressMessages(library(DT))
```
##Adding phantom tools
```{r, message=TRUE, warning=TRUE}
#In order to get dinamic javascript object install those ones. If you get problems installing go to Stackoverflow.com and type your error to discover what to do. In some cases the libraries need to be intalled in outside R libs.
#devtools::install_github("wch/webshot")
#webshot::install_phantomjs()
```
##Setting a random seed - this is a good strategy to keep the same graph pattern layout in a new report generation
```{r, message=TRUE, warning=TRUE}
set.seed(123)
```

##Simplify Graph - removing loops and duble edges 
```{r, echo=T, message=FALSE, warning=FALSE}
full_no_zero<-simplify(full_no_zero) #Simplify
```


#Diameter - length of the longest geodesic.

##Diameter Non-weigthed 
```{r, echo=FALSE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
diameter(full_no_zero)
full_no_zero_dim<-get.diameter(full_no_zero)
full_no_zero_dim
```
##Diameter Weigthed 
```{r, echo=FALSE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
diameter(full_no_zero, weights=E(full_no_zero)$weight)
full_no_zero_dim<-get.diameter(full_no_zero, weights=E(full_no_zero)$weight)
full_no_zero_dim
```
##Plotting Diameter
```{r, echo=FALSE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
#Preparing Nodes
g<-full_no_zero
d <- get.diameter(g)

E(g)$color <- "grey"
E(g)$width <- 1
E(g, path=d)$color <- "red"
E(g, path=d)$width <- 2
V(g)$label.color <- "blue"
V(g)$color  <- "SkyBlue2"
V(g)[ d ]$label.color <- "black"
V(g)[ d ]$color <- "red"

#Plotting
plot(g, 
     layout=layout.kamada.kawai(g), 
     vertex.label.dist=0, 
     layout=layout.kamada.kawai(g),
     vertex.label.color="black",
     vertex.frame.color="#ffffff",
     vertex.label=get.vertex.attribute(g,"LABEL_COR"),
     vertex.size=sqrt(degree(g)),
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(g)+1)/10,
     edge.width=edge.betweenness(g, weights=E(g)$full_no_zero)/500,
     edge.curved = TRUE
     
     )

#Solving Problems with legend rendering 
a<-V(g)$LABEL_COR
b<-V(g)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f.a<-t(e$a)
f.b<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f.a),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(f.b),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Diameter of fuull_no_zero_fancy", sub = "Source: from authors ", xlab="created by igraph 0")
#Adding Stats
  text(x = -1, y = -1.2, labels =sprintf("Diameter: %.2f",diameter(g)))
```

#Saving objects with new variables and changes
```{r, echo=T, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
save.image("~/SNArRDJF/Robject/15_diameter_full_no_zero.RData") 
```


