---
title: "Untitled"
author: "Leonardo Martins"
date: "17 de julho de 2016"
output: html_document
---


####IMPORTANTE Checar q167 toxicomanos  q111 deville  q125 rendição IMPORTANTE######

#1.24. Loading objects generated with 1.Principal.Rmd Script - Please run this script only after run 1.Principal.Rmd
```{r}
load("~/SNArRDJF/1.Principal.RData")
```

##1.25 Reload packages
```{r packages, message=TRUE, warning=TRUE}
require(igraph) #load package for social network analysis
library(dplyr)
library(RColorBrewer)
library(car)
library(xtable)
library(ggplot2)

set.seed(123)
```


#1. Descriptive Analysis for confianca* - Complete Graph - All networks were generated using from this one

###1.1 Vertices and Edges Number
```{r}
#1. Vertices and Edges Number
confianca_vcount<-vcount(confianca)
confianca_ecount<-ecount(confianca)
```
###1.2 Vertice Number
```{r}
vcount(confianca)
```
###1.3 Edge Number
```{r}
ecount(confianca)
```

#2. Centrality Measures

• Undirected graphs:
– Actor centrality - involvement (connections) with other actors

• Directed graphs:
– Actor centrality - source of the ties (outgoing edges)
– Actor prestige - recipient of many ties (incoming edges)

#2. Centrality Degree (number of ties/nearest neighbors).
High centrality degree - direct contact with many other actors
```{r}
#Saving in igrpah object
V(confianca)$indegree<-degree(confianca, mode = "in") # Actor prestige - recipient of many ties (incoming edges)
V(confianca)$outdegree <- degree(confianca, mode = "out") # Actor centrality - source of the ties (outgoing edges)
V(confianca)$totaldegree <- degree(confianca, mode = "total")

#Saving in Global Environment as an object
confianca_indegree<-degree(confianca, mode = "in")
confianca_outdegree<-degree(confianca, mode = "out")
confianca_totaldegree<-degree(confianca, mode = "total")
```

#2.1 Centrality Degree Descriptive Statistics - non-normalized
```{r}
# Centrality Degree Descriptive Statistics
##in
summary(confianca_indegree)
sd(confianca_indegree)
##out
summary(confianca_outdegree)
sd(confianca_outdegree)
##all
summary(confianca_totaldegree)
sd(confianca_totaldegree)

#Histogram confianca degree
hist(degree(confianca, mode = "in", normalized = F), ylab="Frequency", xlab="Degree",  breaks=vcount(confianca)/10, main="Histogram of Indegree Nodes - confianca*")
hist(degree(confianca, mode = "out", normalized = F), ylab="Frequency", xlab="Degree",  breaks=vcount(confianca)/10, main="Histogram of Outdegree Nodes - confianca*")
hist(degree(confianca, mode = "all", normalized = F), ylab="Frequency", xlab="Degree",  breaks=vcount(confianca)/10, main="Histogram of All Degree Nodes - confianca*")
```  

A slightly more nuanced metric is “strength centrality”, which is defined as the sum of the weights of all the connections for a given node. This is also sometimes called “weighted degree centrality”.

#2.1.1 Compute strength - weighted
```{r}
V(confianca)$strength_confianca<- strength(confianca, weights=E(confianca)$confianca)
strength_confianca<- strength(confianca, weights=E(confianca)$confianca)

##Stats
summary(strength_confianca)
sd(strength_confianca)
```

#2.2 Centrality Degree Normalized
```{r}
#Centrality Degree Normalized saving igraph object
V(confianca)$indegree_n<-degree(confianca, mode = "in", normalized = T)
V(confianca)$outdegree_n<- degree(confianca, mode = "out", normalized = T)
V(confianca)$totaldegree_n<- degree(confianca, mode = "total", normalized = T)

#Saving in Global Environment as an object
confianca_indegree_n<-degree(confianca, mode = "in", normalized = T)
confianca_outdegree_n<-degree(confianca, mode = "out", normalized = T)
confianca_totaldegree_n<-degree(confianca, mode = "total", normalized = T)

# Centrality Degree Normalized Descriptive Statistics

##in
summary(confianca_indegree_n)
sd(confianca_indegree_n)
##out
summary(confianca_outdegree_n)
sd(confianca_outdegree_n)
##all
summary(confianca_totaldegree_n)
sd(confianca_totaldegree_n)

#Histogram confianca degree
hist(degree(confianca, mode = "in", normalized = F), ylab="Frequency", xlab="Normalized Degree",  breaks=vcount(confianca)/10, main="Histogram of Normalized Indegree Nodes - confianca*")
hist(degree(confianca, mode = "out", normalized = F), ylab="Frequency", xlab="Normalized Degree",  breaks=vcount(confianca)/10, main="Histogram of Normalized Indegree Nodes - confianca*")
hist(degree(confianca, mode = "all", normalized = F), ylab="Frequency", xlab="Normalized Degree",  breaks=vcount(confianca)/10, main="Histogram of Normalized All Degree Nodes - confianca*")
```

#2.2.1 Centralization Degree
```{r}
V(confianca)$centr_degree_confianca <- centralization.degree(confianca)$res
centr_degree_confianca <- centralization.degree(confianca)

#Centralization
centr_degree_confianca$centralization
#Theoretical Max
centr_degree_confianca$theoretical_max
```

##2.3 Degree distribution considering total equal one
```{r}
## Degree distribution when the totality is considered 1
confianca_degree.distribution<-degree.distribution(confianca)

## Degree distribution Descriptive Stats
summary(confianca_degree.distribution)
sd(confianca_degree.distribution)

#Histogram confianca distribution degree
hist(degree.distribution(confianca), breaks=vcount(confianca)/10, ylab="Frequency", xlab="Degree Distribuition", main="Histogram of Degree Distribuition - confianca*")

#Degree Probability Distribution
dd <- degree.distribution(confianca, cumulative=T, mode="all")
plot(dd, pch=19, cex=1, col="orange", xlab="Degree", ylab="Cumulative Frequency", main= "Cumulative Frequency of confianca* ")
```

#2.4 Log-Log Degree Distribution - Scale Free Network - Does it fit to power law
```{r}
#Log-Log Degree Distribution - Scale Free Network - Does it fit to power law? 
dd.confianca <- degree.distribution(confianca)
d <- 1:max(degree(confianca))-1
ind <- (dd.confianca != 0)

plot(d[ind], 
     dd.confianca[ind], 
     log="xy", 
     col="blue",
     xlab=c("Log-Degree"), 
     ylab=c("Log-Intensity"),
     main="Log-Log Degree Distribution For confianca*"
     )
```

#2.5.1 Average Neighbor Degree versus Vertex Degree (log-log scale for confianca*)
```{r}
#Average Neighbor Degree versus vertex degree (log-log scale for confianca)
a.nn.deg.confianca <- graph.knn(confianca,V(confianca))$knn

#Saving to igraph object
V(confianca)$a.nn.deg.confianca <- a.nn.deg.confianca <- graph.knn(confianca,V(confianca))$knn

#Plotting Average Neighbor Degree versus vertex degree
plot(degree(confianca), 
     a.nn.deg.confianca, 
     log="xy", 
     col="goldenrod", 
     xlab=c("Log Vertex Degree"),
     ylab=c("Log Average Neighbor Degree"),
     main="Average Neighbor Degree vs Vertex Degree - Log-Log Scale for confianca*"
     )
```

#2.5.2 Average Weighted Neighbor Degree versus vertex degree (log-log scale for weighted confianca*)
```{r}
#Average Weighted Neighbor Degree versus vertex degree (log-log scale for confianca)
a.nn.deg.confianca_w <- graph.knn(confianca,V(confianca), weights=E(confianca)$confianca)$knn

#Saving to igraph object
V(confianca)$a.nn.deg.confianca_w <-a.nn.deg.confianca <- graph.knn(confianca,V(confianca), weights=E(confianca)$confianca)$knn

#Average Weighted Neighbor Descriptive
summary(a.nn.deg.confianca_w)
sd(a.nn.deg.confianca_w)

#Plotting Average Neighbor Degree versus vertex degree
plot(degree(confianca), 
     a.nn.deg.confianca, 
     log="xy", 
     col="goldenrod", 
     xlab=c("Log Vertex Degree"),
     ylab=c("Log Average Neighbor Degree"),
     main="Average Weighted Neighbor Degree vs Vertex Degree - Log-Log Scale For Weighted confianca*"
     )
```

#2.6.1 Network plotting based only on degree measures 
```{r}
#Plotting based only on degree measures 
plot(confianca, 
     layout=layout.kamada.kawai(confianca), 
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=degree(confianca)/10,
     vertex.frame.color="#ffffff",
     edge.arrow.size=degree(confianca)/10000,
     vertex.label.cex=degree(confianca)/500,
     edge.width=(edge.betweenness(confianca, weights =E(confianca)$confianca))/500,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$LABEL_COR
b<-V(confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Network Vertex Degree Sized - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median In Degree: %.2f\nMedian Out Degree: %.2f",
     median(degree(confianca, mode="in")), 
     median(degree(confianca, mode="out"))
   ))
```

#2.6.2 Network plotting based only on degree measures 
```{r}
#Get Variable
V(confianca)$confianca_color_degree<-V(confianca)$totaldegree

#Creating brewer pallette
vertex_confianca_color_degree<-
  colorRampPalette(brewer.pal(length(unique(
          V(confianca)$confianca_color_degree)), "RdBu"))(
            length(unique(V(confianca)$confianca_color_degree)))

#Saving as Vertex properties 
V(confianca)$vertex_confianca_color_degree<- vertex_confianca_color_degree[as.numeric(cut(degree(confianca),breaks =length(unique(V(confianca)$confianca_color_degree))))]
   
#Plotting
plot(confianca, 
     layout=layout.kamada.kawai(confianca),
     vertex.color=V(confianca)$vertex_confianca_color_degree,
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=degree(confianca)/10,
     vertex.frame.color="#ffffff",
     edge.arrow.size=0.1,
     vertex.label.cex=(degree(confianca))/800,
     edge.width=(edge.betweenness(confianca, weights =E(confianca)$confianca))/500,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$confianca_color_degree
b<-V(confianca)$vertex_confianca_color_degree
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
e<-e[order(e$a,decreasing=T),] 
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .3)

#Adding Title
  title("Network Vertex Degree Sized and Colored - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median In Degree: %.2f\nMedian Out Degree: %.2f",
     median(degree(confianca, mode="in")), 
     median(degree(confianca, mode="out"))
   ))
```

#2.6.3 Network Plotting Centralization - Degree Measures 
```{r}
#Get Variable
V(confianca)$confianca_color_degree<-V(confianca)$centr_degree_confianca

#Creating brewer pallette
vertex_confianca_color_degree<-
  colorRampPalette(brewer.pal(length(unique(
          V(confianca)$confianca_color_degree)), "Spectral"))(
            length(unique(V(confianca)$confianca_color_degree)))

#Saving as Vertex properties 
V(confianca)$vertex_confianca_color_degree<- vertex_confianca_color_degree[as.numeric(cut(V(confianca)$confianca_color_degree,breaks =length(unique(V(confianca)$confianca_color_degree))))]
   
#Plotting
plot(confianca, 
     #layout=layout.kamada.kawai(confianca),
     vertex.color=V(confianca)$vertex_confianca_color_degree,
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=degree(confianca)/10,
     vertex.frame.color="#ffffff",
     edge.arrow.size=0.1,
     vertex.label.cex=(degree(confianca))/800,
     edge.width=(edge.betweenness(confianca, weights =E(confianca)$confianca))/500,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$confianca_color_degree
b<-V(confianca)$vertex_confianca_color_degree
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
e<-e[order(e$a,decreasing=T),] 
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .3)

#Adding Title
  title("Network Vertex Degree Sized and Colored - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median In Degree: %.2f\nMedian Out Degree: %.2f",
     median(degree(confianca, mode="in")), 
     median(degree(confianca, mode="out"))
   ))
```

#2.6.4 Alternative vizualization using degree in order to genarete sub-graphs - Higher than median degree network
```{r}
# Network elements with lower than meadian degree
lowerthanmedian.network_confianca<-V(confianca)[degree(confianca)<=median(degree(confianca))] 

#Deleting vertices based in intersection betewenn confianca 
small_confianca<-delete.vertices(confianca, lowerthanmedian.network_confianca)

#Plotting 
plot(small_confianca, 
     layout=layout.kamada.kawai(small_confianca), 
     vertex.label=get.vertex.attribute(small_confianca,"LABEL_COR"),
     vertex.size=degree(small_confianca)/10,
     vertex.frame.color="#ffffff",
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(small_confianca))/10,
     edge.width=(edge.betweenness(small_confianca))/500,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(small_confianca)$LABEL_COR
b<-V(small_confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Network Higher Than Median Degree - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median In Degree: %.2f\nMedian Out Degree: %.2f",
     median(degree(small_confianca, mode="in")), 
     median(degree(small_confianca, mode="out"))
   )
  )

```

#2.6.5 Alternative vizualization using degree in order to genarete sub-graphs - Lower than median degree network 
```{r}
# Network elements with lower than meadian degree
lowerthanmedian.network_confianca<-V(confianca)[degree(confianca)>=median(degree(confianca))] 

#Deleting vertices based in intersection betewenn confianca 
small_confianca<-delete.vertices(confianca, lowerthanmedian.network_confianca)

#Plotting 
plot(small_confianca, 
     layout=layout.kamada.kawai(small_confianca), 
     vertex.label=get.vertex.attribute(small_confianca,"LABEL_COR"),
     vertex.size=degree(small_confianca)/2,
     edge.arrow.size=0.1,
     vertex.frame.color="#ffffff",
     vertex.label.degree=(-pi)/2,	
     vertex.label.cex=log(degree(small_confianca)+2)/2,
     edge.width=(edge.betweenness(small_confianca)),
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(small_confianca)$LABEL_COR
b<-V(small_confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Network Lower than Median Degree - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median In Degree: %.2f\nMedian Out Degree: %.2f",
     median(degree(small_confianca, mode="in")), 
     median(degree(small_confianca, mode="out"))
   )
  )
```

#2.6.6 Plotting using Average Neighbor Degree
```{r}
#Plotting based only on degree measures  #a.nn.deg.confianca_w 
plot(confianca, 
     layout=layout.kamada.kawai(confianca), 
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=(graph.knn(confianca,V(confianca))$knn)/10,
     vertex.frame.color="#ffffff",
     edge.arrow.size=0.1,
     vertex.label.cex=sqrt(graph.knn(confianca,V(confianca))$knn)/20,
     edge.width=(edge.betweenness(confianca, weights =E(confianca)$confianca))/500,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$LABEL_COR
b<-V(confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Network Average Neighbor Degree Sized - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median Average Neighbor Degree: %.2f",
     median(graph.knn(confianca,V(confianca))$knn)
   ))
```

#2.6.7 Plotting using Average Weighted Neighbor Degree
```{r}
#Plotting based only on degree measures  a.nn.deg.confianca_w 
plot(confianca, 
     layout=layout.kamada.kawai(confianca), 
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=sqrt(graph.knn(confianca,V(confianca), weights= E(confianca)$confianca)$knn),
     vertex.frame.color="#ffffff",
     edge.arrow.size=0.1,
     vertex.label.cex=log(graph.knn(confianca,V(confianca), weights= E(confianca)$confianca)$knn)/10,
     edge.width=edge.betweenness(confianca, weights =E(confianca)$confianca)/500,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$LABEL_COR
b<-V(confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Network Average Weighted Neighbor Degree Sized - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median Average Weighte Neighbor Degree: %.2f",
     median(graph.knn(confianca,V(confianca), weights= E(confianca)$confianca)$knn)
   ))
```

#2.6.8 Circle Degree ***Too intensive computation*** #code
```{r}
#Circle Degree ***Too intense computation***
#A_confianca <- get.adjacency(confianca, sparse=FALSE)
#library(network)
#g <- network::as.network.matrix(A_confianca)
#library(sna)
#sna::gplot.target(g, degree(g), main="Degree",
#circ.lab = FALSE, circ.col="skyblue",
#usearrows = FALSE,
#vertex.col=c("blue", rep("red", 32), "yellow"),
#edge.col="darkgray")
```

#2.7 Closeness - centrality based on distance to others in the graph - How close an actor to all the other actors in network.

High closeness centrality - short communication path to others, minimal number of steps to reach others.

Answers the “Kevin Bacon” question:
“How many steps are required to access every other vertex from a given vertex?”

One practical implication of this metric: it helps you gauge how information might spread within your network, and who might be the best people to leverage if you need to make sure information gets around. (http://www.tc.umn.edu/~alink/R-social-network-analysis.html)

Closeness centrality can be defined as a measure of how far other nodes are from the node in question. Nodes with high closeness centrality are likely to be relatively efficient in receiving or transmitting information to/from distant parts of the social network.

Scores may be interpreted as arising from a reciprocal process in which the centrality of each actor is proportional to the sum of the centralities of those actors to whom he or she is connected. In general, vertices with high eigenvector centralities are those which are connected to many other vertices which are, in turn, connected to many others (and so on). (The perceptive may realize that this implies that the largest values will be obtained by individuals in large cliques (or high-density substructures)

#2.7.1 Closeness Non-normalized
```{r}
#Closeness Non-normalized

#Saving to Igraph object
V(confianca)$incloseness <- closeness(confianca, mode = "in") #%>% round(6)
V(confianca)$outcloseness <- closeness(confianca, mode = "out") #%>% round(6)
V(confianca)$totalcloseness <- closeness(confianca, mode = "total") #%>% round(4)

#Saving to Environment
confianca_incloseness<- closeness(confianca, mode = "in") #%>% round(6)
confianca_outcloseness<- closeness(confianca, mode = "out") #%>% round(6)
confianca_totalcloseness<- closeness(confianca, mode = "total") #%>% round(6)

##in
summary(confianca_incloseness)
sd(confianca_incloseness)

##out
summary(confianca_outcloseness)
sd(confianca_outcloseness)

##all
summary(confianca_totalcloseness)
sd(confianca_totalcloseness)
```

#2.7.2 Closeness Non-normalized 
```{r}
#Closeness Normalized

#Saving to Igraph object
V(confianca)$incloseness_n <- closeness(confianca, mode = "in", normalized = T) #%>% round(6)
V(confianca)$outcloseness_n <- closeness(confianca, mode = "out", normalized = T) #%>% round(6)
V(confianca)$totalcloseness_n <- closeness(confianca, mode = "total", normalized = T) #%>% round(6)

#Saving to Environment
confianca_incloseness_n<- closeness(confianca, mode = "in", normalized = T) #%>% round(6)
confianca_outcloseness_n<- closeness(confianca, mode = "out", normalized = T) #%>% round(6)
confianca_totalcloseness_n<- closeness(confianca, mode = "total", normalized = T) #%>% round(6)

##in
summary(confianca_incloseness_n)
sd(confianca_incloseness_n)

##out
summary(confianca_outcloseness_n)
sd(confianca_outcloseness_n)

##all
summary(confianca_totalcloseness_n)
sd(confianca_totalcloseness_n)
```


#2.7.3 Closeness normalized weighted 
```{r}
#Closeness Normalized weighted - it only makes sense with var>7 or acesso and confianca - even though its here to make as a first script draft

#Saving to Igraph object
V(confianca)$incloseness_w <- closeness(confianca, mode = "in", normalized = T, weights=E(confianca)$confianca) #%>% round(6)
V(confianca)$outcloseness_w <- closeness(confianca, mode = "out", normalized = T,weights=E(confianca)$confianca) #%>% round(6)
V(confianca)$totalcloseness_w <- closeness(confianca, mode = "total", normalized = T, weights=E(confianca)$confianca) #%>% round(6)

#Saving to Environment
confianca_incloseness_w<- closeness(confianca, mode = "in", normalized = T, weights=E(confianca)$confianca) #%>% round(6)
confianca_outcloseness_w<- closeness(confianca, mode = "out", normalized = T, weights=E(confianca)$confianca) #%>% round(6)
confianca_totalcloseness_w<- closeness(confianca, mode = "total", normalized = T, weights=E(confianca)$confianca) #%>% round(6)

##in
summary(confianca_incloseness_w)
sd(confianca_incloseness_w)

##out
summary(confianca_outcloseness_w)
sd(confianca_outcloseness_w)

##all
summary(confianca_totalcloseness_w)
sd(confianca_totalcloseness_w)
```

#2.7.4 Closeness Weighted for all vertex 
```{r}
V(confianca)$closeness_stats_confianca_w <- closeness(confianca, vids = V(confianca), mode = "all", weights =V(confianca)$confianca, normalized = FALSE)

closeness_stats_confianca_w <- closeness(confianca, vids = V(confianca), mode = "all", weights =V(confianca)$confianca, normalized = FALSE)
```

#2.7.5 Centralization Closseness
```{r}
V(confianca)$centr_closeness_confianca <- centralization.closeness(confianca)$res
centr_closeness_confianca <- centralization.closeness(confianca)

#Centralization
centr_closeness_confianca$centralization
#Theoretical Max
centr_closeness_confianca$theoretical_max
```

#2.7.6 Network Plotting Based On Closeness 
```{r}
#Get Variable
V(confianca)$confianca_color_degree<-round(V(confianca)$totalcloseness,4)

#Creating brewer pallette
vertex_confianca_color_degree<-
  colorRampPalette(brewer.pal(length(unique(
          V(confianca)$confianca_color_degree)), "RdBu"))(
            length(unique(V(confianca)$confianca_color_degree)))

#Saving as Vertex properties 
V(confianca)$vertex_confianca_color_degree<-
  vertex_confianca_color_degree[as.numeric(
  cut(V(confianca)$confianca_color_degree,
      breaks=length(unique(V(confianca)$confianca_color_degree))))]

#Plotting
plot(confianca, 
     layout=layout.kamada.kawai(confianca),
     vertex.color=V(confianca)$vertex_confianca_color_degree,
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=closeness(confianca)*4000,
     vertex.frame.color="#ffffff",
     edge.arrow.size=0.1,
     vertex.label.cex=(closeness(confianca))/80,
     edge.width=(edge.betweenness(confianca, weights =E(confianca)$confianca))/500,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$confianca_color_degree
b<-V(confianca)$vertex_confianca_color_degree
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
e<-e[order(e$a,decreasing=T),] 
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .3)

#Adding Title
  title("Network Closeness Degree Sized and Colored - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median In Closennes: %.4f\nMedian Out Closennes: %.4f",
     median(closeness(confianca, mode="in")), 
     median(closeness(confianca, mode="out"))
   ))
```

#2.7.6 Network Plotting Based On Centralization Closeness 
```{r}
#Get Variable
V(confianca)$confianca_color_degree<-round(V(confianca)$centr_closeness_confianca,3)

#Creating brewer pallette
vertex_confianca_color_degree<-
  colorRampPalette(brewer.pal(length(unique(
          V(confianca)$confianca_color_degree)), "Spectral"))(
            length(unique(V(confianca)$confianca_color_degree)))

#Saving as Vertex properties 
V(confianca)$vertex_confianca_color_degree<-
  vertex_confianca_color_degree[as.numeric(
  cut(V(confianca)$confianca_color_degree,
      breaks=length(unique(V(confianca)$confianca_color_degree))))]

#Plotting
plot(confianca, 
     layout=layout.kamada.kawai(confianca),
     vertex.color=V(confianca)$vertex_confianca_color_degree,
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=centralization.closeness(confianca)$res*20,
     vertex.frame.color="#ffffff",
     edge.arrow.size=0.1,
     vertex.label.cex=centralization.closeness(confianca)$res,
     edge.width=(edge.betweenness(confianca, weights =E(confianca)$confianca))/500,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$confianca_color_degree
b<-V(confianca)$vertex_confianca_color_degree
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
e<-e[order(e$a,decreasing=T),] 
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1.25, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .3)

#Adding Title
  title("Network Centralization Closeness - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median In Closennes: %.4f\nMedian Out Closennes: %.4f",
     median(closeness(confianca, mode="in")), 
     median(closeness(confianca, mode="out"))
   ))
```

#2.8 Betweenness - Number of shortest paths going through the actor σst(i)

High betweenness centrality - vertex lies on many shortest paths. Probability that a communication from s
to t will go through i.

Betweenness measures the number of shortest paths between nodes in the network that go through the node in question. Nodes with relatively high betweenness are likely to be key conduits of information flow across a network, and their removal may have a large impact on spreading phenomena.

#2.8.1 Betweenness Centrality - (Vertex)
```{r}
#Betweenness centrality based on a broker position connecting others or Number of geodesics that pass through the node or the edge.

#Betweenness - number of geodesics (shortest paths) going through a vertex - A higher number means an more important node.
V(confianca)$betweenness <- betweenness(confianca) %>% round(1)
confianca_betweenness <- betweenness(confianca) %>% round(1)

##all
summary(confianca_betweenness)
sd(confianca_betweenness)
```

#2.8.2 Betweenness Centrality Weighted - (Vertex)
```{r}
V(confianca)$betweenness_confianca_w <- betweenness(confianca, weights=E(confianca)$confianca) %>% round(1)

betweenness_confianca_w <- betweenness(confianca, weights=E(confianca)$confianca) %>% round(1)

##all
summary(betweenness_confianca_w)
sd(betweenness_confianca_w)
```

#2.8.3 Centralization Betweenness
```{r}
V(confianca)$centr_betweenness_confianca <- centralization.betweenness(confianca)$res
centr_betweenness_confianca <- centralization.betweenness(confianca)

#Centralization
centr_betweenness_confianca$centralization
#Theoretical Max
centr_betweenness_confianca$theoretical_max
```

#2.8.1 Plotting Betweenness Centrality - (Vertex)
```{r}
#Plotting based only on betweenness measures 
plot(confianca, 
     layout=layout.kamada.kawai(confianca), 
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=betweenness(confianca)/500,
     edge.arrow.size=0.1,
     vertex.label.cex=(betweenness(confianca)+1)/10000,
     edge.width=log(edge.betweenness(confianca, weights =E(confianca)$confianca))/50,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$LABEL_COR
b<-V(confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Network Vertex Betweenness Sized - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median Betweenness: %.2f\nSD Betweenness: %.2f",
     median(betweenness(confianca)), 
     sd(betweenness(confianca))
   ))
```

#2.8.2 Network Plotting Based On Centralization Betweenness
```{r}
#Get Variable
V(confianca)$confianca_color_degree<-round(V(confianca)$centr_betweenness_confianca,3)

#Creating brewer pallette
vertex_confianca_color_degree<-
  colorRampPalette(brewer.pal(length(unique(
          V(confianca)$confianca_color_degree)), "Spectral"))(
            length(unique(V(confianca)$confianca_color_degree)))

#Saving as Vertex properties 
V(confianca)$vertex_confianca_color_degree<-
  vertex_confianca_color_degree[as.numeric(
  cut(V(confianca)$confianca_color_degree,
      breaks=length(unique(V(confianca)$confianca_color_degree))))]

#Plotting
plot(confianca, 
     layout=layout.kamada.kawai(confianca),
     vertex.color=V(confianca)$vertex_confianca_color_degree,
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=(centralization.betweenness(confianca)$res)/500,
     vertex.frame.color="#ffffff",
     edge.arrow.size=0.1,
     vertex.label.cex=(centralization.betweenness(confianca)$res + 1)/10000,
     edge.width=(edge.betweenness(confianca, weights =E(confianca)$confianca))/500,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$confianca_color_degree
b<-V(confianca)$vertex_confianca_color_degree
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
e<-e[order(e$a,decreasing=T),] 
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1.25, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .3)

#Adding Title
  title("Network Centralization Betweenness - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median Betweenness: %.0f\nSD Betweenness: %.0f",
     median(betweenness(confianca)), 
     sd(betweenness(confianca))
   ))
```

#2.9 Eigenvector - centrality proportional to the sum of connection centralities - Values of the first eigenvector of the graph matrix.

#2.9.1 Eigen Centrality - Saving objects
```{r}
#Eigen_Centrality 
V(confianca)$eigenvector <- eigen_centrality(confianca, directed = TRUE, weights = V(confianca)$confianca) %$% vector %>% round(3)

confianca_eigenvector <- eigen_centrality(confianca, directed = TRUE, weights = V(confianca)$confianca) %$% vector %>% round(3)

#Eigenvalue Calculated Eigenvector
confianca_eigenvector_value <- eigen_centrality(confianca, directed = TRUE, weights = V(confianca)$confianca) %$% value %>% round(3) # The eigenvalue corresponding to the calculated eigenvector, i.e. the centrality scores.
```

#2.9.2 Eigen Centrality Descriptive
```{r}
#all
summary(confianca_eigenvector)
sd(confianca_eigenvector)

#Eigenvalue Calculated Eigenvector
confianca_eigenvector_value
```

#2.9.3 Centralization EigenVector - how central the most central node in the network in relation to all other nodes.
```{r}
V(confianca)$centr_eigen_confianca <- centr_eigen(confianca, directed = T)$vector
centr_eigen_confianca <-centr_eigen(confianca, directed = T)$vector
#Centralization
centr_eigen(confianca, directed = T)$centralization
#Max
centr_eigen(confianca, directed = T)$theoretical_max
```

##2.9.4 Plotting based only on Eigenvector Centrality measures 
```{r}
#Plotting based only on Eigen Centrality measures 
plot(confianca, 
     layout=layout.kamada.kawai(confianca), 
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=(eigen_centrality(confianca)$vector)*20,
     vertex.frame.color="#ffffff",
     edge.arrow.size=0.1,
     vertex.label.cex=sqrt(eigen_centrality(confianca)$vector)/2,
     edge.width=edge.betweenness(confianca, weights =E(confianca)$confianca)/500,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$LABEL_COR
b<-V(confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Eigenvector Centrality Measure - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median Eigenvector: %.2f",
     median(eigen_centrality(confianca)$vector)
   ))
```

#2.9.4 Network Plotting Based On Centralization Eigenvector
```{r}
#Get Variable
V(confianca)$confianca_color_degree<-round(centr_eigen(confianca, directed = T)$vector,2)

#Creating brewer pallette
vertex_confianca_color_degree<-
  colorRampPalette(brewer.pal(length(unique(
          V(confianca)$confianca_color_degree)), "Spectral"))(
            length(unique(V(confianca)$confianca_color_degree)))

#Saving as Vertex properties 
V(confianca)$vertex_confianca_color_degree<-
  vertex_confianca_color_degree[as.numeric(
  cut(V(confianca)$confianca_color_degree,
      breaks=length(unique(V(confianca)$confianca_color_degree))))]

#Plotting
plot(confianca, 
     layout=layout.kamada.kawai(confianca),
     vertex.color=V(confianca)$vertex_confianca_color_degree,
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=centr_eigen(confianca, directed = T)$vector*25,
     vertex.frame.color="#ffffff",
     edge.arrow.size=0.1,
     vertex.label.cex=(centr_eigen(confianca, directed = T)$vector + 1)/10,
     edge.width=(edge.betweenness(confianca, weights =E(confianca)$confianca))/500,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$confianca_color_degree
b<-V(confianca)$vertex_confianca_color_degree
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
e<-e[order(e$a,decreasing=T),] 
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1.25, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .3)

#Adding Title
  title("Network Centralization Betweenness - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median Betweenness: %.0f\nSD Betweenness: %.0f",
     median(betweenness(confianca)), 
     sd(betweenness(confianca))
   ))
```

#2.8.1 Bonacich's Power Centrality Scores of Network Positions

Each node's centrality score depends both on how many connections it has and how many connections its connections have.
“It doesn't only matter how many friends you have. It matters how many friends your friends have.” *http://www.leonidzhukov.net/hse/2014/socialnetworks/papers/Bonacich-Centrality.pdf*

#Power (beta) Centrality Stats
```{r, results="asis"}
#Saving power as an object
power_centrality_stats_confianca <- power_centrality(confianca, nodes = V(confianca), loops = FALSE, exponent = 1, rescale = FALSE, tol = 1e-07, sparse = TRUE)

#Saving power as an igraph attributte
V(confianca)$power_centrality_stats_confianca <-power_centrality(confianca, nodes = V(confianca), loops = FALSE, exponent = 1, rescale = FALSE, tol = 1e-07, sparse = TRUE) 

#Or are you more powerful if you're connected to weak, dependent people? (negative attenuation factor)
i=sort(power_centrality_stats_confianca) %>% round(3)
table_i<-cbind(V(confianca)$V5_LABEL_LABEL,i)
colnames(table_i) <- c("ID", "Power")
table_i10<-table_i[1:10,]
toptable_i10 <- xtable(table_i10)
print(toptable_i10 , floating=FALSE, type="html")

#Are you more powerful if you're connected to powerful people? (positive attenuation factor)
d=sort(power_centrality_stats_confianca, decreasing = T) %>% round(3)
table_d<-cbind(V(confianca)$V5_LABEL_LABEL,d)
colnames(table_d) <- c("ID", "Power")
table_d10<-table_d[1:10,]
toptable_d10 <- xtable(table_d10)
print(toptable_d10, floating=FALSE, type="html")
```

#2.8.3 #Setting color for each vertex based on Power
```{r}
# Set colors to plot distances:
V(confianca)$power_centrality_stats_confianca_r<-round(V(confianca)$power_centrality_stats_confianca,0)

# Creating brewer pallette
vertex_col_spower <- colorRampPalette(brewer.pal(length(unique(V(confianca)$power_centrality_stats_confianca_r)), "Blues"))(length(unique(V(confianca)$power_centrality_stats_confianca_r))) 

#Saving as Vertex properties                                   
V(confianca)$color_spower <- vertex_col_spower[factor(V(confianca)$power_centrality_stats_confianca_r)]  
```

#2.8.3 Plotting Power Centrality Degree
```{r}
plot(confianca, 
     layout=layout.kamada.kawai(confianca), 
     vertex.color=V(confianca)$color_spower, 
     vertex.label=V(confianca)$V5_LABEL_LABEL,
     vertex.frame.color="#ffffff",
     vertex.label.color="black",
     vertex.size=sqrt((power_centrality(confianca)^2))*5,
     edge.arrow.size=0.1,
     vertex.label.cex=sqrt((power_centrality(confianca)+1)^2)/10,
     edge.width=edge.betweenness(confianca, weights =E(confianca)$confianca)/500,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$power_centrality_stats_confianca_r
b<-V(confianca)$color_spower
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .5)

#Adding Title
  title("Bonacich Power Centrality Scores of Network Positions - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median Power Degree: %.2f\n SD Power Degree:%.2f",
     median(power_centrality_stats_confianca),sd(power_centrality_stats_confianca)
     ))
```

#2.8.2 Alpha Bonacich's centrality scores of network positions
```{r, results="asis"}
#Saving power as an object
alpha_centrality_stats_confianca <- alpha_centrality(confianca, loops = FALSE, alpha = 1, exo = 1, weights = V(confianca)$confianca, tol = 1e-07, sparse = TRUE)

#Saving power as an igraph attributte
V(confianca)$alpha_centrality_stats_confianca<-alpha_centrality(confianca, loops = FALSE, alpha = 1, exo = 1, weights = V(confianca)$confianca, tol = 1e-07, sparse = TRUE)

#Descriptive 
summary(alpha_centrality_stats_confianca)
sd(alpha_centrality_stats_confianca)

#Or are you more powerful if you're connected to weak, dependent people? (negative attenuation factor)
i=sort(alpha_centrality_stats_confianca) %>% round(3)
table_i<-cbind(V(confianca)$V5_LABEL_LABEL,i)
colnames(table_i) <- c("ID", "Alpha")
table_i10<-table_d[1:10,]
toptable_i <- xtable(table_i)
print(toptable_i , floating=FALSE, type="html")

#Are you more powerful if you're connected to powerful people? (positive attenuation factor)
d=sort(alpha_centrality_stats_confianca, decreasing = T) %>% round(3)
table_d<-cbind(V(confianca)$V5_LABEL_LABEL,d)
colnames(table_d) <- c("ID", "Power")
table_d10<-table_d[1:10,]
toptable_d <- xtable(table_d)
print(toptable_d , floating=FALSE, type="html")
```

#2.8.3 #Setting color for each vertex based on Alpha
```{r}
# Set colors to plot distances:
V(confianca)$alpha_centrality_stats_confianca_r<-round(V(confianca)$alpha_centrality_stats_confianca,0)

# Creating brewer pallette
vertex_col_s <- colorRampPalette(brewer.pal(length(unique(V(confianca)$alpha_centrality_stats_confianca_r)), "YlOrRd"))(length(unique(V(confianca)$alpha_centrality_stats_confianca_r))) 

#Saving as Vertex properties                                                                  
V(confianca)$color_s <- vertex_col_s[factor(V(confianca)$alpha_centrality_stats_confianca_r)]  
```

#2.8.3 Plotting Alpha Centrality Degree
```{r}
plot(confianca, 
     layout=layout.kamada.kawai(confianca), 
     vertex.color=V(confianca)$color_s, 
     vertex.label=V(confianca)$V5_LABEL_LABEL,
     vertex.label.color="black",
     vertex.frame.color="#ffffff",
     vertex.size=sqrt((alpha_centrality(confianca, weights = V(confianca)$confianca)^2)),
     edge.arrow.size=0.1,
     vertex.label.cex=sqrt((alpha_centrality(confianca))^2)/50,
     edge.width=edge.betweenness(confianca, weights =E(confianca)$confianca)/500,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$alpha_centrality_stats_confianca_r
b<-V(confianca)$color_s
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .5)

#Adding Title
  title("Bonacich's Alpha Centrality Scores of Network Positions - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median Alpha Degree: %.2f\n SD Alpha Degree:%.2f",
     median(alpha_centrality_stats_confianca),sd(alpha_centrality_stats_confianca)
     ))
```

#2.10 Hubs and Authorities (HITS)

Citation networks. Reviews vs original research (authoritative) papers
• authorities, contain useful information
• hubs, contains links to authorities
• Good authorities referred by good hubs
• Good hubs point to good authorities

#2.10.1 Hubs - are expected to contain catalogs with a large number of outgoing links; 
```{r}
#Kleinberg’s hub scores
V(confianca)$hub <- hub.score(confianca)$vector
confianca_hub<- hub.score(confianca)$vector

#stats
summary(confianca_hub)
sd(confianca_hub)

#Plotting based only on degree measures 
plot(confianca, 
     layout=layout.kamada.kawai(confianca), 
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=10*sqrt(hub.score(confianca)$vector),
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(confianca))/10,
     edge.width=log(edge.betweenness(confianca, weights =E(confianca)$confianca))/5,
     edge.curved = TRUE)

#Solving Problems with legend rendering 
a<-V(confianca)$LABEL_COR
b<-V(confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Network Hub Sized - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Mean Hub Score: %.2f\n SD Hub Score: %.2f",
     mean(confianca_hub),
     sd(confianca_hub)))
```

#2.10.2 Authorities would get many incoming links from hubs, presumably because of their high-quality relevant information.
```{r}
#Kleinberg’s authority scores
V(confianca)$authority.score<- authority.score(confianca)$vector
confianca_auth <- authority.score(confianca)$vector
#stats
summary(confianca_auth)
sd(confianca_auth)

#Plotting based only on Authorities Scores 
plot(confianca, 
     layout=layout.kamada.kawai(confianca), 
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=10*sqrt(authority.score(confianca)$vector),
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(confianca))/10,
     edge.width=log(edge.betweenness(confianca, weights =E(confianca)$confianca))/5,
     edge.curved = TRUE)

#Solving Problems with legend rendering 
a<-V(confianca)$LABEL_COR
b<-V(confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Network Authorities Scores  Sized - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Mean Authorities Scores: %.2f\n SD Authorities Scores: %.2f",
     mean(confianca_auth),
     sd(confianca_auth)))
```

#2.10.3 Google PageRank 
```{r}
#PageRank
V(confianca)$page.rank<-page.rank(confianca)$vector
confianca_pr<-page.rank(confianca)$vector
#stats
summary(confianca_pr)
sd(confianca_pr)


#Plotting based only on Authorities Scores 
plot(confianca, 
     layout=layout.kamada.kawai(confianca), 
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=30*sqrt(page.rank(confianca)$vecto),
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(confianca))/10,
     edge.width=log(edge.betweenness(confianca, weights =E(confianca)$confianca))/100,
     edge.curved = TRUE)

#Solving Problems with legend rendering 
a<-V(confianca)$LABEL_COR
b<-V(confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Network Google Page Rank Sized - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Mean Page Rank Scores: %.2f\n SD Page Rank Scores: %.2f",
     mean(confianca_pr),
     sd(confianca_pr)))
```

#Plotting HITS by Degree
```{r}
# We will plot 6 graphs in 2 rows and 3 columns:

prPB<-page_rank(confianca)$vector
hPB<-hub.score(confianca)$vector
authPB<-authority.score(confianca)$vector
indegPB<-degree(confianca, mode="in")
outdegPB<-degree(confianca, mode="out")

op <- par(mfrow = c(2, 3))
plot(prPB, hPB, xlab="PageRank", ylab="Hubs", col="blue")
plot(prPB, authPB, xlab="PageRank", ylab="Authorities", col="blue") 
plot(hPB, authPB, xlab="Hubs", ylab="Authorities", col="blue") 
plot(indegPB, outdegPB, xlab="In- degree", ylab="Out- degree", col="blue") 
plot(indegPB, authPB, xlab="In- degree", ylab="Authorities", col="blue")
plot(outdegPB, hPB, xlab="Out- degree", ylab="Hubs", col="blue")
par(op)
```



```{r}
#For in-degrees:
indegnamesPB=which(indegPB>sort(indegPB)[vcount(confianca)-5]) #For out- degrees:
outdegnamesPB=which(outdegPB>sort(outdegPB)[vcount(confianca)-5]) #For PageRank:
prnamesPB=which(prPB>sort(prPB)[vcount(confianca)-5]) #For Hubs:
hnamesPB=which(hPB>sort(hPB)[vcount(confianca)-5]) #For Authorities:
authnamesPB=which(authPB>sort(authPB)[vcount(confianca)-5])
##Create a matrix to output:
topnamesPB=cbind(indegnamesPB, authnamesPB, prnamesPB, outdegnamesPB, hnamesPB)
#Assign column names:
colnames(topnamesPB) <- c("In- degree", "Authorities", "PageRank", "Out- degree", "Hubs")
row.names(topnamesPB) <- c("q163_Assistência.Hospitalar...Hospital.de.Pronto.Socorro...HPS", "q192_Ambulatório.de.Saúde.Mental...Centro.de.Atenção.à.Saúde.Mental..CASM.", "q170_CAPS...CAPS.AD", "q191_Urgência.Emergência...Serviço.de.Atendimento.Móvel.de.Urgência..SAMU.", "171_CAPS...CAPS.Casa.Viva")

topnamesPB
```


##2.10.3.1 Ego Network CAPSAD - Example considering its high page rank
#2.10.3.1.1 All connections 
```{r}
#Making igrpah ego object
make_ego_graph_all_confianca<-make_ego_graph(confianca, order=1, V(confianca)[V2_LABEL_ID=="q170_CAPS...CAPS.AD"], mode ="all", mindist = 0)[[1]]

#Plotting ego based on Page Rank 
plot(make_ego_graph_all_confianca, 
     layout=layout.kamada.kawai(make_ego_graph_all_confianca), 
     vertex.label=get.vertex.attribute(make_ego_graph_all_confianca,"LABEL_COR"),
     vertex.size=30*sqrt(page.rank(make_ego_graph_all_confianca)$vector),
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(make_ego_graph_all_confianca))/10,
     edge.width=log(edge.betweenness(make_ego_graph_all_confianca))/100,
     edge.curved = TRUE)

#Solving Problems with legend rendering 
a<-V(make_ego_graph_all_confianca)$LABEL_COR
b<-V(make_ego_graph_all_confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Ego Network Page Rank Sized - All connections from CAPSAD - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Mean Page Rank Scores: %.2f\n SD Page Rank Scores: %.2f",
     mean(page.rank(make_ego_graph_all_confianca)$vector),
     sd(page.rank(make_ego_graph_all_confianca)$vector)
     ))
```

#2.10.3.1.2 Out connections 
```{r}
#Making igrpah ego object
make_ego_graph_out_confianca<-make_ego_graph(confianca, order=1, V(confianca)[V2_LABEL_ID=="q170_CAPS...CAPS.AD"], mode ="out", mindist = 0)[[1]]

#Plotting ego based on Page Rank 
plot(make_ego_graph_out_confianca, 
     layout=layout.kamada.kawai(make_ego_graph_out_confianca), 
     vertex.label=get.vertex.attribute(make_ego_graph_out_confianca,"LABEL_COR"),
     vertex.size=30*sqrt(page.rank(make_ego_graph_out_confianca)$vector),
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(make_ego_graph_out_confianca))/10,
     edge.width=log(edge.betweenness(make_ego_graph_out_confianca))/100,
     edge.curved = TRUE)

#Solving Problems with legend rendering 
a<-V(make_ego_graph_out_confianca)$LABEL_COR
b<-V(make_ego_graph_out_confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Ego Network Page Rank Sized - Out Connections from CAPSAD - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Mean Page Rank Scores: %.2f\n SD Page Rank Scores: %.2f",
     mean(page.rank(make_ego_graph_out_confianca)$vector),
     sd(page.rank(make_ego_graph_out_confianca)$vector)
     ))
```

#2.10.3.1.3 - In connections 
```{r}
#Making igrpah ego object
make_ego_graph_in_confianca<-make_ego_graph(confianca, order=1, V(confianca)[V2_LABEL_ID=="q170_CAPS...CAPS.AD"], mode ="in", mindist = 0)[[1]]

#Plotting ego based on Page Rank 
plot(make_ego_graph_in_confianca, 
     layout=layout.kamada.kawai(make_ego_graph_in_confianca), 
     vertex.label=get.vertex.attribute(make_ego_graph_in_confianca,"LABEL_COR"),
     vertex.size=30*sqrt(page.rank(make_ego_graph_in_confianca)$vector),
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(make_ego_graph_in_confianca))/10,
     edge.width=log(edge.betweenness(make_ego_graph_in_confianca))/100,
     edge.curved = TRUE)

#Solving Problems with legend rendering 
a<-V(make_ego_graph_in_confianca)$LABEL_COR
b<-V(make_ego_graph_in_confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Ego Network CAPS AD Page Rank Sized - In connections from CAPS AD - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Mean Page Rank Scores: %.2f\n SD Page Rank Scores: %.2f",
     mean(page.rank(make_ego_graph_in_confianca)$vector),
     sd(page.rank(make_ego_graph_in_confianca)$vector)
     ))
```

##2.10.4 Removing CAPSAD from its own ego network-  Example considering its high page rank and resilience test
```{r}
#Making igrpah ego object
make_ego_graph_all_confianca_without_CAPSAD<-delete_vertices(make_ego_graph_all_confianca,V(make_ego_graph_all_confianca)[V2_LABEL_ID=="q170_CAPS...CAPS.AD"])

#Plotting ego based on Page Rank 
plot(make_ego_graph_all_confianca_without_CAPSAD, 
     layout=layout.kamada.kawai(make_ego_graph_all_confianca_without_CAPSAD), 
     vertex.label=get.vertex.attribute(make_ego_graph_all_confianca_without_CAPSAD,"LABEL_COR"),
     vertex.size=30*sqrt(page.rank(make_ego_graph_all_confianca_without_CAPSAD)$vector),
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(make_ego_graph_all_confianca_without_CAPSAD))/10,
     edge.width=log(edge.betweenness(make_ego_graph_all_confianca_without_CAPSAD))/10,
     edge.curved = TRUE)

#Solving Problems with legend rendering 
a<-V(make_ego_graph_all_confianca_without_CAPSAD)$LABEL_COR
b<-V(make_ego_graph_all_confianca_without_CAPSAD)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Ego Network CAPS AD Page Rank Sized - All Connections Removing CAPS AD - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Mean Page Rank Scores: %.2f\n SD Page Rank Scores: %.2f",
     mean(page.rank(make_ego_graph_all_confianca_without_CAPSAD)$vector),
     sd(page.rank(make_ego_graph_all_confianca_without_CAPSAD)$vector)
     ))
```


##2.10.5 Removing complex services from CAPSAD ego network -  Example considering its high page rank and resilience test (!= CAPSAD, PRONTO-SOCORRO, AMBULATÓRIO, SAMU)
```{r}
#Making igrpah ego object - without (!= CAPSAD, PRONTO-SOCORRO, AMBULATÓRIO, SAMU)

#Removing high complex services

make_ego_graph_all_confianca_without_complex<-
  delete_vertices(make_ego_graph_all_confianca,
                  c(V(make_ego_graph_all_confianca)
                  [V2_LABEL_ID=="q170_CAPS...CAPS.AD"],#Removing CAPSAD - Psychosocial Treatment Center
                  V(make_ego_graph_all_confianca)
                  [V2_LABEL_ID=="q163_Assistência.Hospitalar...Hospital.de.Pronto.Socorro...HPS"], #Removing PRONTO-SOCORRO - Emergency Hospital
                  V(make_ego_graph_all_confianca)
                  [V2_LABEL_ID=="q192_Ambulatório.de.Saúde.Mental...Centro.de.Atenção.à.Saúde.Mental..CASM."],#Removing AMBULATÓRIO - Outpatient Center
                  V(make_ego_graph_all_confianca)
                  [V2_LABEL_ID=="q191_Urgência.Emergência...Serviço.de.Atendimento.Móvel.de.Urgência..SAMU."] #Removing SAMU - Emergency Mobile Service ? WTF
                  ))


#Plotting ego based on Page Rank 
plot(make_ego_graph_all_confianca_without_complex, 
     layout=layout.kamada.kawai(make_ego_graph_all_confianca_without_complex), 
     vertex.label=get.vertex.attribute(make_ego_graph_all_confianca_without_complex,"LABEL_COR"),
     vertex.size=30*sqrt(page.rank(make_ego_graph_all_confianca_without_complex)$vector),
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(make_ego_graph_all_confianca_without_complex))/10,
     edge.width=log(edge.betweenness(make_ego_graph_all_confianca_without_complex))/10,
     edge.curved = TRUE)

#Solving Problems with legend rendering 
a<-V(make_ego_graph_all_confianca_without_complex)$LABEL_COR
b<-V(make_ego_graph_all_confianca_without_complex)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Ego Network CAPS AD Page Rank Sized - All Connections Removing High Complex Service - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Mean Page Rank Scores: %.2f\n SD Page Rank Scores: %.2f",
     mean(page.rank(make_ego_graph_all_confianca_without_complex)$vector),
     sd(page.rank(make_ego_graph_all_confianca_without_complex)$vector)
     ))
```

#2.11.1 Minimum spanning tree non-normalized that connects all the vertices together with the minimal total edges. - it seems that we have a problem with legends - check this out further
```{r}
#Creating Minimum spanning tree
msp_confianca<-mst(confianca)

#Plotting based only on degree measures 
plot(msp_confianca, 
     layout=layout.kamada.kawai(msp_confianca), 
     vertex.label=get.vertex.attribute(msp_confianca,"LABEL_COR"),
     vertex.size=sqrt(degree(msp_confianca)),
     edge.arrow.size=0.1,
     vertex.label.cex=sqrt(degree(msp_confianca))/50,
     edge.width=log(edge.betweenness(msp_confianca, weights =E(msp_confianca)$msp_confianca))/5,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(msp_confianca)$LABEL_COR
b<-V(msp_confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Minimum Spanning Tree Non-normalized - from confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median In Degree: %.2f\nMedian Out Degree: %.2f",
     median(degree(msp_confianca, mode="in")), 
     median(degree(msp_confianca, mode="out"))
   ))
```

#2.11.2 Minimum weighted spanning tree that connects all the vertices together with the minimal total weighting for its edges. - it seems that we have a problem with legends - check this out further
```{r}
#Creating Minimum weighted spanning tree
msp_confianca_w<-minimum.spanning.tree(confianca, weights=1/edge.betweenness(confianca, weights =E(confianca)$confianca), algorithm='prim')

#Weight edges are considered here as barries as we are trying to find the easiest path with minimal weight - so considering the inverse of weight (1/weight) are we using "unacess" and "untrust" as barries - this would cool   

#Plotting based only on degree measures 
plot(msp_confianca_w, 
     layout=layout.kamada.kawai(msp_confianca_w), 
     vertex.label=get.vertex.attribute(msp_confianca_w,"LABEL_COR"),
     vertex.size=sqrt(degree(msp_confianca_w)),
     edge.arrow.size=0.1,
     vertex.label.cex=sqrt(degree(msp_confianca_w))/20,
     edge.width=1/edge.betweenness(msp_confianca_w, weights =E(msp_confianca_w)$msp_confianca_w),
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(msp_confianca_w)$LABEL_COR
b<-V(msp_confianca_w)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Minimum Weighted Spanning Tree (Edge Betweenness) - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median In Degree: %.2f\nMedian Out Degree: %.2f",
     median(degree(msp_confianca_w, mode="in")), 
     median(degree(msp_confianca_w, mode="out"))
   ))
```

#3. The proportion of present edges from all possible edges in the network.
#3.1 Edge Density
```{r}
#Edge Density
edge_density_confianca<-edge_density(confianca) #The proportion of present edges from all possible edges in the network.

# Density - same as above
graph.density(confianca)
```

#3.2.1 Reciprocity Default
```{r}
# Reciprocity Default - Proportion of mutual connections - probability that hte opposite counterpart of a directed graph is also included
reciprocity(confianca, mode="default")
```

#3.2.2 Reciprocity Ratio
```{r}
# Reciprocity Ratio - Probability  of mutual connections between a vertex pair - if we know - probability that hte opposite counterpart of a directed graph is also included in the 
reciprocity(confianca, mode="ratio")
```

#3.3 Connected components
```{r}
#Is connected - decides whether the graph is weakly or strongly connected.
is.connected(confianca) #trick information - let's check this out further
```

#3.3.1 Strong Connected Components
```{r}
#Strong Connected
components_strong_confianca<-components(confianca, mode="strong")
V(confianca)$components_strong_confianca_membership<-components_strong_confianca$membership # adding to igraph object

#Number of clusters
count_components(confianca)

#Display components structure
components_strong_confianca
```

#3.3.2 Plotting connected strong components using membership
```{r}
#Plotting based only on degree measures 
plot(confianca, 
     layout=layout.kamada.kawai(confianca), 
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=sqrt(degree(confianca)),
     mark.groups = by(seq_along(components_strong_confianca$membership),
                      components_strong_confianca$membership, 
                      invisible),   ## Add community indicating background colors
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(confianca)+1)/10,
     edge.width=edge.betweenness(confianca, weights =E(confianca)$confianca)/500,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$LABEL_COR
b<-V(confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Network Vertex Degree Sized - Classfied by Components Structure - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median In Degree: %.2f\nMedian Out Degree: %.2f",
     median(degree(confianca, mode="in")), 
     median(degree(confianca, mode="out"))
   ))
```

#3.4 Dyad Census
```{r}
#Dyad Census (Number of pairs with mutual connections "mut" and number of pairs with non-mutual connections "asym")
dyad.census_confianca<-dyad.census(confianca)

# Calculating reciprocity - just as an example
2*dyad_census(confianca)$mut/ecount(confianca) # Calculating reciprocity
```

#3.4.1 Dyad Census classified by mutal non-mutual and no connection
```{r}
#3.4 Dyad Census
#Dyad - Classify dyads in a directed graphs

#The number of pairs with mutual connections.
dyad.census_confianca_mut<-dyad.census_confianca$mut
dyad.census_confianca_mut

#The number of pairs with non-mutual connections.
dyad.census_confianca_asym<-dyad.census_confianca$asym
dyad.census_confianca_asym

#The number of pairs with no connection between them.
dyad.census_confianca_null<-dyad.census_confianca$null
dyad.census_confianca_null
```

#3.5 - Triad Census - Check this out in order to understand triad lables *http://www.stats.ox.ac.uk/~snijders/Trans_Triads_ha.pdf* - page 15
```{r}
#Triad Census 
tc_confianca <- triad.census(confianca)

#Triad Census Label 
census_labels = c('003',
                  '012',
                  '102',
                  '021D',
                  '021U',
                  '021C',
                  '111D',
                  '111U',
                  '030T',
                  '030C',
                  '201',
                  '120D',
                  '120U',
                  '120C',
                  '210',
                  '300')

#Saving in a dataframe for further studies
triad_df_confianca <- data.frame(census_labels,tc_confianca)
write.csv(triad_df_confianca, "~/SNArRDJF/Banco Redes R/confianca_complet_triads.csv)
```

#3.5.1 - Triad Census Types 
```{r}
#Describing triads
triad_df_confianca
```


#3.7 Distances and paths - shortest distance between each pair of nodes in the network (in both directions for directed graphs).

#3.7.1 Average path length between any two given nodes - calculates the average path length in a graph, by calculating the shortest paths between all pairs of vertices (both ways for directed graphs). This function does not consider edge weights currently and uses a breadth-first search
```{r}
#Average path length
mean_distance(confianca, directed=T, unconnected = T)
```


#3.7.2 Shortest Paths
```{r}
#Shortest Paths
confianca_sp_in <- shortest.paths(confianca, mode='in', weights=V(confianca)$confianca) # sames as bellow
confianca_sp_out <- shortest.paths(confianca, mode='out', weights=V(confianca)$confianca) #same as above
confianca_sp_all <- shortest.paths(confianca, mode='all', weights=V(confianca)$confianca) # all

#in
mean(confianca_sp_in[which(confianca_sp_in != Inf)])
sd(confianca_sp_in[which(confianca_sp_in != Inf)])

#out
mean(confianca_sp_out[which(confianca_sp_out != Inf)])
sd(confianca_sp_out[which(confianca_sp_out != Inf)])

#all
mean(confianca_sp_out[which(confianca_sp_out != Inf)])
sd(confianca_sp_out[which(confianca_sp_out != Inf)])
```


#3.7.3 Length of all shortest paths in the graph:
```{r}
#All shortest paths 
distances_sp_all_confianca<-distances(confianca, mode="all", weights=E(confianca)$confianca)
#distances_sp_all_confianca

#In shortest paths 
distances_sp_in_confianca<-distances(confianca, mode="in",weights=E(confianca)$confianca)
#distances_sp_in_confianca

#Out shortest paths 
distances_sp_out_confianca<-distances(confianca, mode="out", weights=E(confianca)$confianca)
#distances_sp_out_confianca
```

#3.7.4 Histogram from shortest path length between each pair of vertices. 
```{r}
distance_table(confianca, directed = TRUE)
```

#3.7.5 Distance from CAPSAD - just as an example for futher explortion
```{r}
#Setting distance from an vertex

confianca_dist.from.CAPSAD <- distances(confianca, v=V(confianca)[V2_LABEL_ID=="q170_CAPS...CAPS.AD"], to=V(confianca), weights=V(confianca)$confianca)

#Saving distance on igraph object 
V(confianca)$confianca_dist.from.CAPSAD<-confianca_dist.from.CAPSAD

# Set colors to plot distances:
oranges <- colorRampPalette(c("dark red", "gold"))
col <- oranges(max(confianca_dist.from.CAPSAD)+1)
col <- col[confianca_dist.from.CAPSAD+1]

#Saving as Vertex properties
V(confianca)$col<-col


#Plotting distance from CAPSAD 
plot(confianca, 
     layout=layout.kamada.kawai(confianca), 
     vertex.color=col, 
     vertex.label=confianca_dist.from.CAPSAD,
     vertex.label.color="white",
     vertex.size=sqrt(degree(confianca)),
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(confianca))/10,
     edge.width=log(edge.betweenness(confianca, weights =E(confianca)$confianca))/5,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$confianca_dist.from.CAPSAD
b<-V(confianca)$col
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Distance from CAPS AD - confianca*", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Avarege path length: %.2f",
     mean_distance(confianca, directed=T, unconnected = T)))
```

#3.8 Reachability Function 
```{r}
#Declaring Reachability function 
reachability <- function(g, m) {
  reach_mat = matrix(nrow = vcount(g), ncol = vcount(g))
  for (i in 1:vcount(g)) {
    reach_mat[i,] = 0
    this_node_reach <- subcomponent(g, i, mode = m) # used "i" instead of "(i - 1)"
    
    for (j in 1:(length(this_node_reach))){
      alter = this_node_reach[j]# removed "+ 1"
      reach_mat[i, alter] = 1
      }
    }
  return(reach_mat)
  }
 
#Reachability
confianca_reach_in <- reachability(confianca, 'in')
confianca_reach_out <- reachability(confianca, 'out')

#in
mean(confianca_reach_in[which(confianca_reach_in != Inf)])
sd(confianca_reach_in[which(confianca_reach_in != Inf)])

#out
mean(confianca_reach_out[which(confianca_reach_out != Inf)])
sd(confianca_reach_out[which(confianca_reach_out != Inf)])
```


#3.9 Subgroups and communities
```{r}
confianca_u <- as.undirected(confianca, mode= "collapse",
                         edge.attr.comb=list(weight="sum", "ignore"))
```

#3.9.1
#Find cliques (complete subgraphs of an undirected graph)
```{r}
cliques_confianca_u<-cliques(confianca_u) # list of cliques       
cliques_confianca_u_size<-sapply(cliques(confianca_u), length) # clique sizes
largest_cliques(confianca_u) # cliques with max number of nodes
```

#3.9.2 Counting cliques
```{r}
#Size of largest clique 
clique_num(confianca_u)
#Number of maximal cliques
count_max_cliques(confianca_u)
```

#3.9.3 Finding the largest cliques - important to consider connectivite 
```{r}
#Generating undirected graph
as.undirected_confianca_u<-as.undirected(confianca_u)

#Coloring largest clique as gold and others one as gray
vcol <- rep("grey80", vcount(confianca_u))
vcol[unlist(largest_cliques(confianca_u))] <- "gold"

#Saving gray and gold as igraph attribute
V(as.undirected_confianca_u)$vcol<-vcol

#Saving labels to display as legend
V(as.undirected_confianca_u)$vcollabel <- recode(V(as.undirected_confianca_u)$vcol, "'gold' = 'Largest Clique'; else= 'Others'")

#Plotting based only on degree measures 
plot(as.undirected(confianca_u), 
     layout=layout.kamada.kawai(as.undirected(confianca_u)), 
     vertex.label=get.vertex.attribute(as.undirected(confianca_u),"LABEL_COR"),
     vertex.color=vcol,
     vertex.size=sqrt(degree(as.undirected(confianca_u))),
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(as.undirected(confianca_u)))/10,
     edge.width=log(edge.betweenness(as.undirected(confianca_u), weights =E(as.undirected(confianca_u))$confianca))/5,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(as.undirected_confianca_u)$vcollabel
b<-V(as.undirected_confianca_u)$vcol
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Network Vertex Degree Sized - classfied by largest clique vs. others", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Size of largest clique: %.1f\nNumber of maximal cliques: %.1f",
     clique_num(confianca_u), 
     count_max_cliques(confianca_u)
   ))
```


#3.10 Betweenness Edges
```{r}
#Edge Betweenness
E(confianca)$edge.btweenness<-edge.betweenness(confianca, weights =E(confianca)$confianca)
confianca_edge.betweenness <-edge.betweenness(confianca, weights =E(confianca)$confianca)

#Edge Betweenness Descriptive
summary(confianca_edge.betweenness)
sd(confianca_edge.betweenness)

#Edge Betweenness order - Tenth higher
E(confianca)[order(confianca_edge.betweenness, decreasing=T)[1:10]]
```

#3.10.1 Community detection (using edge betweenness)
```{r}
## Community structure detection based on edge betweenness
communityEdgeBetwn_confianca <- edge.betweenness.community(confianca)
confianca_edge.betweenness.community <- edge.betweenness.community(confianca)

#Creating communities
V(confianca)$edge.betweenness.community <- membership(confianca_edge.betweenness.community)
confianca_edge.betweenness.community <- membership(confianca_edge.betweenness.community)
```

#3.10.2 Plotting community by using edge betweenness
```{r}
#Plotting based only on degree measures 
plot(confianca, 
     layout=layout.kamada.kawai(confianca), 
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=sqrt(degree(confianca)),
     mark.groups = by(seq_along(confianca_edge.betweenness.community),
                      confianca_edge.betweenness.community, 
                      invisible),   ## Add community indicating background colors
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(confianca))/10,
     edge.width=log(edge.betweenness(confianca, weights =E(confianca)$confianca))/5,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$LABEL_COR
b<-V(confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Network Vertex Degree Sized - Classfied by Communities using Edges Betweenness", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median In Degree: %.2f\nMedian Out Degree: %.2f",
     median(degree(confianca, mode="in")), 
     median(degree(confianca, mode="out"))
   ))
```

#3.11.Community detection (Random walk)
```{r}
#Community detection (Random walk)
confianca_walktrap.community <- walktrap.community(confianca)
```

#3.11.1 Network Dendograma
```{r}
dend.g.network_confianca <- as.dendrogram(confianca_walktrap.community, se.modularity=TRUE)
plot(dend.g.network_confianca, main = "Dendrograma confianca", nodePar=list(pch=c(NA, 20)))
```

#3.11.2 Saving Random walk community
```{r}
V(confianca)$walktrap.community <- membership(confianca_walktrap.community)
confianca_walktrap.community <- membership(confianca_walktrap.community)
```

#3.11.3 Plotting Random walk community 
```{r}
#Plotting based only on degree measures 
plot(confianca, 
     layout=layout.kamada.kawai(confianca), 
     vertex.label=get.vertex.attribute(confianca,"LABEL_COR"),
     vertex.size=sqrt(degree(confianca)),
     mark.groups = by(seq_along(confianca_walktrap.community),
                      confianca_walktrap.community, 
                      invisible),   ## Add community indicating background colors
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(confianca))/10,
     edge.width=log(edge.betweenness(confianca, weights =E(confianca)$confianca))/5,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(confianca)$LABEL_COR
b<-V(confianca)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Network Vertex Degree Sized - Classfied by Communities using Random Walk", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median In Degree: %.2f\nMedian Out Degree: %.2f",
     median(degree(confianca, mode="in")), 
     median(degree(confianca, mode="out"))
   ))
```


#3.12 Decomposed Graph 
```{r}
comps_confianca <- decompose.graph(confianca)
sapply(comps_confianca, diameter)
table(sapply(comps_confianca, vcount))
```

#3.12.1 Getting Plotting Decomposed Graphs

```{r}
comps_confianca1<-comps_confianca[[1]]
#comps_confianca2<-comps_confianca[[2]]
#comps_confianca3<-comps_confianca[[3]]
#comps_confianca4<-comps_confianca[[4]]
#comps_confianca5<-comps_confianca[[5]]
#comps_confianca6<-comps_confianca[[6]]
#comps_confianca7<-comps_confianca[[7]]
#comps_confianca8<-comps_confianca[[8]]
#...
```

#3.12.2 Plotting based Decomposed Graphs
```{r}
#Plotting based Decomposed Graphs
plot(comps_confianca1, 
     layout=layout.kamada.kawai(comps_confianca1), 
     vertex.label=get.vertex.attribute(comps_confianca1,"LABEL_COR"),
     vertex.size=sqrt(degree(comps_confianca1)),
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(comps_confianca1))/10,
     edge.width=log(edge.betweenness(comps_confianca1, weights=E(comps_confianca1)$comps_confianca1))/5,
     edge.curved = TRUE
     )

#Solving Problems with legend rendering 
a<-V(comps_confianca1)$LABEL_COR
b<-V(comps_confianca1)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Network Vertex Degree Sized - Classfied by Communities using Decomposed", sub = "Source: from authors ")
  text(x = -1, y = -1.2, labels = 
   sprintf("Median In Degree: %.2f\nMedian Out Degree: %.2f",
     median(degree(comps_confianca1, mode="in")), 
     median(degree(comps_confianca1, mode="out"))
   ))
```

#3.13 Transitivity - clustering coefficient
```{r}
# Transitivity Global
#Net is treated as an undirected network global - ratio of triangles (direction disregarded) to connected triples.

#Non-weighted 
transitivity(confianca, weights=E(confianca)$confianca, type="global")

#Weighted
transitivity(confianca, weights=E(confianca)$confianca,type="weighted")
transitivity(confianca, weights=E(confianca)$confianca,type="global")


# Transitivity Local - Ratio of triangles to connected triples each vertex is part of.

#Transitivity Local - Non-weighted
V(confianca)$transitivity_local<-transitivity(confianca, type="local") 
transitivity_local<-transitivity(confianca, type="local") #local - ratio of triangles to connected triples each vertex is part of.

#Descriptive Statistics for Local Transitivity by Vertex 
summary(transitivity_local[which(transitivity_local != Inf)])
sd(transitivity_local[which(transitivity_local != Inf)])
 

#Transitivity Barrat Weighted
V(confianca)$transitivity_local_w<-transitivity(confianca, type="barrat") 
transitivity_local_w<-transitivity(confianca, weights=E(confianca)$confianca, type="barrat")

#Descriptive Statistics for Barrat Weighted Transitivity by Vertex 
summary(transitivity_local_w[which(transitivity_local_w != Inf)])
sd(transitivity_local_w[which(transitivity_local_w != Inf)])
```

#3.14 Optimal Community - too intense
```{r}
#V(confianca)$optimal_comm_confianca <- #membership(optimal.community(confianca))
#optimal_comm_confianca <- membership(optimal.community(confianca))
```

#3.14 Diameter - length of the longest geodesic.
```{r}
#Diameter Non-weigthed 
diameter(confianca)
confianca_dim<-get.diameter(confianca)
confianca_dim

#Diameter Weigthed 
diameter(confianca, weights=E(confianca)$confianca)
confianca_dim<-get.diameter(confianca, weights=E(confianca)$confianca)
confianca_dim
```

#3.14.1 Plotting Diameter
```{r}
#Preparing Nodes
g<-confianca
d <- get.diameter(g)

E(g)$color <- "grey"
E(g)$width <- 1
E(g, path=d)$color <- "red"
E(g, path=d)$width <- 2
V(g)$label.color <- "blue"
V(g)$color  <- "SkyBlue2"
V(g)[ d ]$label.color <- "black"
V(g)[ d ]$color <- "red"

#Plotting
plot(g, 
     layout=layout.kamada.kawai(g), 
     vertex.label.dist=0, 
     layout=layout.kamada.kawai(g),
     vertex.label=get.vertex.attribute(g,"LABEL_COR"),
     vertex.size=sqrt(degree(g)),
     edge.arrow.size=0.1,
     vertex.label.cex=log(degree(g)+1)/10,
     edge.width=edge.betweenness(g, weights=E(g)$confianca)/500,
     edge.curved = TRUE
     
     )

#Solving Problems with legend rendering 
a<-V(g)$LABEL_COR
b<-V(g)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f.a<-t(e$a)
f.b<-t(e$b)

#Adding Legend
legend(x=1, y=1.25,
       legend=as.character(f.a),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(f.b),
       pt.cex=4,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .8)

#Adding Title
  title("Diameter of confianca*", sub = "Source: from authors ", xlab="created by igraph 0")
#Adding Stats
  text(x = -1, y = -1.2, labels =sprintf("Diameter: %.2f",diameter(g)))
```

#3.15 Maximal Independence Vertex Sets - return a set of vertex if there no edges between any two vertices in it ***Too Intense Calculation - commented code*** 
```{r}
#Maximal Independence Vertex Sets
#independence.number(confianca)
```

```{r}
# Re-generate dataframes for both nodes and edges, now containing
# calculated network attributes
node_list <- get.data.frame(confianca, what = "vertices")

#Writing Node CSV 
write.csv2(node_list, "~/SNArRDJF/Banco Redes R/Networks/node_confianca.csv", fileEncoding = "macintosh")

# Edge List
edge_list <- get.data.frame(confianca, what = "edges") %>%
  inner_join(node_list %>% select(name, walktrap.community), by = c("from" = "name")) %>%
  inner_join(node_list %>% select(name, walktrap.community), by = c("to" = "name")) %>%
  mutate(group = ifelse(walktrap.community.x == walktrap.community.y, walktrap.community.x, NA) %>% factor())

#Writing Edge List CSV
write.csv2(edge_list, "~/SNArRDJF/Banco Redes R/Networks/edge_confianca.csv", fileEncoding = "macintosh")


# Create a character vector containing every node name
all_nodes <- sort(node_list$name)

# Adjust the 'to' and 'from' factor levels so they are equal
# to this complete list of node names
plot_data <- edge_list %>% mutate(
        to = factor(to, levels = all_nodes),
        from = factor(from, levels = all_nodes))

# Create the adjacency matrix plot
ggplot(plot_data, aes(x = from, y = to, fill = group)) +
      geom_raster() +
      theme_bw() +
      # Because we need the x and y axis to display every node,
      # not just the nodes that have connections to each other,
      # make sure that ggplot does not drop unused factor levels
      scale_x_discrete(drop = FALSE) +
      scale_y_discrete(drop = FALSE) +
      theme(
        # Rotate the x-axis lables so they are legible
        axis.text.x = element_text(angle = 270, hjust = 0),
        # Force the plot into a square aspect ratio
        aspect.ratio = 1,
        # Hide the legend (optional)
        legend.position = "none")


#Create a character vector of node names sorted by their
# community membership. Here, I rearrange the node_list
# table by the "comm" variable, then extract the
# "name" vector
name_order <- (node_list %>% arrange(walktrap.community))$name

# Reorder edge_list "from" and "to" factor levels based on
# this new name_order
plot_data <- edge_list %>% mutate(
        to = factor(to, levels = name_order),
        from = factor(from, levels = name_order))


# Create the adjacency matrix plot
ggplot(plot_data, aes(x = from, y = to, fill = group)) +
      geom_raster() +
      theme_bw() +
      # Because we need the x and y axis to display every node,
      # not just the nodes that have connections to each other,
      # make sure that ggplot does not drop unused factor levels
      scale_x_discrete(drop = FALSE) +
      scale_y_discrete(drop = FALSE) +
      theme(
        # Rotate the x-axis lables so they are legible
        axis.text.x = element_text(angle = 270, hjust = 0),
        # Force the plot into a square aspect ratio
        aspect.ratio = 1,
        # Hide the legend (optional)
        legend.position = "none")

# Now run the ggplot code again
```

#4. Saving objects with new variables and changes
```{r}
save.image("~/SNArRDJF/2.SNA.RData") 
load("~/SNArRDJF/2.SNA.RData")# just in case 
```



