---
title: "Banco de Dados Redes"
author: "Leonardo Martins"
date: "17 de maio de 2016"
output: html_document
---

```{r packages}
setwd('~/Banco Redes R')
require(XLConnect)
require(readxl)
require(psych)
require(igraph) #load package for social network analysis
require(networkD3) #load package for sankey network
library(rgexf)
library(reshape2)

suppressMessages(library(igraph))
suppressMessages(library(miniCRAN))
suppressMessages(library(magrittr))
suppressMessages(library(keyplayer))
suppressMessages(library(dplyr))
library(feather)
suppressMessages(library(visNetwork))
library(knitr)
suppressMessages(library(DT))

```


```{r functions}
# Building read excel allsheets 
read_excel_allsheets <- function(filename) 
{
    sheets <- readxl::excel_sheets(filename)
    x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
    names(x) <- sheets
    x
}
```

## Open each datatable in a different file

```{r}
#Creating a list with all spreadsheet
mysheets <- read_excel_allsheets("base.xlsx")
```

```{r pressure, echo=FALSE}

#Creating each .csv file with mysheets names
for (i in names(mysheets)) 
{
    filename = paste(i, ".csv", sep="")
    write.csv2(mysheets[[i]], filename)
}

#Creating each .csv file with numbered sheets 
#for (i in seq_along(mysheets))
#{
#    filename = paste(i, ".csv", sep="")
#    write.csv2(mysheets[[i]], filename)
#}

#In order to improve data manipulation - open each as an object in R Global Envirowment
#list2env(mysheets,envir=.GlobalEnv)


#Creating a new mysheets with seq_along in order to keep some objects with numbered titles - in case of doubt - use Dicionário de Matrizes file. 
#mysheets->mynumbered
#Duplicating mysheets and transforming it in a new numbered list 
#paste("o",seq_along(mynumbered), sep="") -> names(mynumbered)
#list2env(mynumbered,envir=.GlobalEnv)
```

```{r}

#Importing Dataframe
importa_matrix2 <- function(x)
{
x<-as.matrix(assign(x, read.table(x,sep=";", stringsAsFactors=FALSE, header = T)))[,-c(1)]
}

importa_matrix3 <- function(x)
{
x<-as.matrix(assign(x, read.table(x,sep=";", stringsAsFactors=FALSE, header = T, row.names=2)))[-c(70, 105, 109, 126, 131, 133, 154, 166),-c(1)]
}

#Importing Matrix 
importa_matrix <- function(x)
{
x<-as.matrix(assign(x, read.table(x,sep=";", stringsAsFactors=FALSE, header = T, row.names=2)))[-c(70, 105, 109, 126, 131, 133, 154, 166),-c(1,71, 106, 110, 127, 132, 134, 155, 167)]
}

```

```{r}
#temp = list.files(pattern="*.csv")
#for (i in 1:8) assign(temp[i], read.table(temp[i],sep=";", stringsAsFactors=FALSE, header = T, #row.names=1))
#for (i in paste(c(1:10),".csv", sep="")) as.matrix(assign(temp[i], read.table(temp[i],sep=";", #stringsAsFactors=FALSE, header = T))
```

```{r}
#Importando bases
Casos_Excluidos_Linha_e_Colun.csv<-importa_matrix2("Casos Excluídos - Linha e Colun.csv")
Dicionário_de_dados_choices.csv<-importa_matrix2("Dicionário de dados - choices.csv")
Dicionário_de_dados_survey.csv<-importa_matrix2("Dicionário de dados - survey.csv")
Dicionário_Matrizes.csv<-importa_matrix2("Dicionário Matrizes.csv")
Nó_simplificado_com_GEOCODE.csv<-importa_matrix2("Nó simplificado com GEOCODE.csv")
Nós_Completo.csv<-importa_matrix2("Nós Completo.csv")
Nós_Simplificado.csv<-importa_matrix2("Nós Simplificado.csv")
attributes.csv<-importa_matrix3("Atributos.csv")
attributes_dic.csv<-importa_matrix2("Dicionário de dados - atributos.csv")
Matriz_x2.csv<-importa_matrix("Matriz x2.csv")
Matriz_0.csv<-importa_matrix("Matriz 0.csv")
Matriz_1.csv<-importa_matrix("Matriz 1.csv")
Matriz_2.csv<-importa_matrix("Matriz 2.csv")
Matriz_3.csv<-importa_matrix("Matriz 3.csv")
Matriz_4.csv<-importa_matrix("Matriz 4.csv")
Matriz_5.csv<-importa_matrix("Matriz 5.csv")
Matriz_6.csv<-importa_matrix("Matriz 6.csv")
Matriz_7.csv<-importa_matrix("Matriz 7.csv")
Matriz_8.csv<-importa_matrix("Matriz 8.csv")
Matriz_9.csv<-importa_matrix("Matriz 9.csv")
Matriz_10.csv<-importa_matrix("Matriz 10.csv")
Matriz_11.csv<-importa_matrix("Matriz 11.csv")
Matriz_12.csv<-importa_matrix("Matriz 12.csv")
Matriz_13.csv<-importa_matrix("Matriz 13.csv")
Matriz_14.csv<-importa_matrix("Matriz 14.csv")
Matriz_15.csv<-importa_matrix("Matriz 15.csv")
Matriz_16.csv<-importa_matrix("Matriz 16.csv")
Matriz_17.csv<-importa_matrix("Matriz 17.csv")
Matriz_18.csv<-importa_matrix("Matriz 18.csv")
Matriz_19.csv<-importa_matrix("Matriz 19.csv")
Matriz_20.csv<-importa_matrix("Matriz 20.csv")
Matriz_21.csv<-importa_matrix("Matriz 21.csv")
Matriz_22.csv<-importa_matrix("Matriz 22.csv")
Matriz_23.csv<-importa_matrix("Matriz 23.csv")
Matriz_24.csv<-importa_matrix("Matriz 24.csv")
atividade= as.matrix(`Matriz_1.csv` + `Matriz_2.csv` + `Matriz_3.csv` + `Matriz_4.csv`+ `Matriz_5.csv`+ `Matriz_6.csv`)
acesso= as.matrix(`Matriz_7.csv` + `Matriz_8.csv` + `Matriz_9.csv` + `Matriz_10.csv`+ `Matriz_11.csv`+ `Matriz_12.csv` + `Matriz_13.csv` + `Matriz_14.csv` + `Matriz_15.csv` + `Matriz_16.csv`)
confianca=as.matrix(`Matriz_17.csv` + `Matriz_18.csv` + `Matriz_19.csv` + `Matriz_20.csv` + `Matriz_21.csv` + `Matriz_22.csv` + `Matriz_23.csv` + `Matriz_24.csv`)
total= as.matrix(atividade + acesso + confianca)
```

```{r}
gMatriz_x2.csv<-graph_from_adjacency_matrix(Matriz_x2.csv, mode="directed",weighted=T,diag=F)
gMatriz_0.csv<-graph_from_adjacency_matrix(Matriz_0.csv, mode="directed",weighted=T,diag=F)
gMatriz_1.csv<-graph_from_adjacency_matrix(Matriz_1.csv, mode="directed",weighted=T,diag=F)
gMatriz_2.csv<-graph_from_adjacency_matrix(Matriz_2.csv, mode="directed",weighted=T,diag=F)
gMatriz_3.csv<-graph_from_adjacency_matrix(Matriz_3.csv, mode="directed",weighted=T,diag=F)
gMatriz_4.csv<-graph_from_adjacency_matrix(Matriz_4.csv, mode="directed",weighted=T,diag=F)
gMatriz_5.csv<-graph_from_adjacency_matrix(Matriz_5.csv, mode="directed",weighted=T,diag=F)
gMatriz_6.csv<-graph_from_adjacency_matrix(Matriz_6.csv, mode="directed",weighted=T,diag=F)
gMatriz_7.csv<-graph_from_adjacency_matrix(Matriz_7.csv, mode="directed",weighted=T,diag=F)
gMatriz_8.csv<-graph_from_adjacency_matrix(Matriz_8.csv, mode="directed",weighted=T,diag=F)
gMatriz_9.csv<-graph_from_adjacency_matrix(Matriz_9.csv, mode="directed",weighted=T,diag=F)
gMatriz_10.csv<-graph_from_adjacency_matrix(Matriz_10.csv, mode="directed",weighted=T,diag=F)
gMatriz_11.csv<-graph_from_adjacency_matrix(Matriz_11.csv, mode="directed",weighted=T,diag=F)
gMatriz_12.csv<-graph_from_adjacency_matrix(Matriz_12.csv, mode="directed",weighted=T,diag=F)
gMatriz_13.csv<-graph_from_adjacency_matrix(Matriz_13.csv, mode="directed",weighted=T,diag=F)
gMatriz_14.csv<-graph_from_adjacency_matrix(Matriz_14.csv, mode="directed",weighted=T,diag=F)
gMatriz_15.csv<-graph_from_adjacency_matrix(Matriz_15.csv, mode="directed",weighted=T,diag=F)
gMatriz_16.csv<-graph_from_adjacency_matrix(Matriz_16.csv, mode="directed",weighted=T,diag=F)
gMatriz_17.csv<-graph_from_adjacency_matrix(Matriz_17.csv, mode="directed",weighted=T,diag=F)
gMatriz_18.csv<-graph_from_adjacency_matrix(Matriz_18.csv, mode="directed",weighted=T,diag=F)
gMatriz_19.csv<-graph_from_adjacency_matrix(Matriz_19.csv, mode="directed",weighted=T,diag=F)
gMatriz_20.csv<-graph_from_adjacency_matrix(Matriz_20.csv, mode="directed",weighted=T,diag=F)
gMatriz_21.csv<-graph_from_adjacency_matrix(Matriz_21.csv, mode="directed",weighted=T,diag=F)
gMatriz_22.csv<-graph_from_adjacency_matrix(Matriz_22.csv, mode="directed",weighted=T,diag=F)
gMatriz_23.csv<-graph_from_adjacency_matrix(Matriz_23.csv, mode="directed",weighted=T,diag=F)
gMatriz_24.csv<-graph_from_adjacency_matrix(Matriz_24.csv, mode="directed",weighted=T,diag=F)
gMatriz_atividade.csv<-graph_from_adjacency_matrix(atividade, mode="directed",weighted=T,diag=F)
gMatriz_acesso.csv<-graph_from_adjacency_matrix(acesso, mode="directed",weighted=T,diag=F)
gMatriz_confianca.csv<-graph_from_adjacency_matrix(confianca, mode="directed",weighted=T,diag=F)
gMatriz_total.csv<-graph_from_adjacency_matrix(total, mode="directed",weighted=T,diag=F)
```

```{r}
gMatriz_x2.txt<-melt(Matriz_x2.csv)
gMatriz_0.txt<-melt(Matriz_0.csv)
gMatriz_1.txt<-melt(Matriz_1.csv)
gMatriz_2.txt<-melt(Matriz_2.csv)
gMatriz_3.txt<-melt(Matriz_3.csv)
gMatriz_4.txt<-melt(Matriz_4.csv)
gMatriz_5.txt<-melt(Matriz_5.csv)
gMatriz_6.txt<-melt(Matriz_6.csv)
gMatriz_7.txt<-melt(Matriz_7.csv)
gMatriz_8.txt<-melt(Matriz_8.csv)
gMatriz_9.txt<-melt(Matriz_9.csv)
gMatriz_10.txt<-melt(Matriz_10.csv)
gMatriz_11.txt<-melt(Matriz_11.csv)
gMatriz_12.txt<-melt(Matriz_12.csv)
gMatriz_13.txt<-melt(Matriz_13.csv)
gMatriz_14.txt<-melt(Matriz_14.csv)
gMatriz_15.txt<-melt(Matriz_15.csv)
gMatriz_16.txt<-melt(Matriz_16.csv)
gMatriz_17.txt<-melt(Matriz_17.csv)
gMatriz_18.txt<-melt(Matriz_18.csv)
gMatriz_19.txt<-melt(Matriz_19.csv)
gMatriz_20.txt<-melt(Matriz_20.csv)
gMatriz_21.txt<-melt(Matriz_21.csv)
gMatriz_22.txt<-melt(Matriz_22.csv)
gMatriz_23.txt<-melt(Matriz_23.csv)
gMatriz_24.txt<-melt(Matriz_24.csv)
gMatriz_atividade.txt<-melt(atividade)
gMatriz_acesso.txt<-melt(acesso)
gMatriz_confianca.txt<-melt(confianca)
gMatriz_total.txt<-melt(total)
```

```{r}
colnames(gMatriz_x2.txt)<-c('from','to','x2')
colnames(gMatriz_0.txt)<-c('from','to','var0')
colnames(gMatriz_1.txt)<-c('from','to','var1')
colnames(gMatriz_2.txt)<-c('from','to','var2')
colnames(gMatriz_3.txt)<-c('from','to','var3')
colnames(gMatriz_4.txt)<-c('from','to','var4')
colnames(gMatriz_5.txt)<-c('from','to','var5')
colnames(gMatriz_6.txt)<-c('from','to','var6')
colnames(gMatriz_7.txt)<-c('from','to','var7')
colnames(gMatriz_8.txt)<-c('from','to','var8')
colnames(gMatriz_9.txt)<-c('from','to','var9')
colnames(gMatriz_10.txt)<-c('from','to','var10')
colnames(gMatriz_11.txt)<-c('from','to','var11')
colnames(gMatriz_12.txt)<-c('from','to','var12')
colnames(gMatriz_13.txt)<-c('from','to','var13')
colnames(gMatriz_14.txt)<-c('from','to','var14')
colnames(gMatriz_15.txt)<-c('from','to','var15')
colnames(gMatriz_16.txt)<-c('from','to','var16')
colnames(gMatriz_17.txt)<-c('from','to','var17')
colnames(gMatriz_18.txt)<-c('from','to','var18')
colnames(gMatriz_19.txt)<-c('from','to','var19')
colnames(gMatriz_20.txt)<-c('from','to','var20')
colnames(gMatriz_21.txt)<-c('from','to','var21')
colnames(gMatriz_22.txt)<-c('from','to','var22')
colnames(gMatriz_23.txt)<-c('from','to','var23')
colnames(gMatriz_24.txt)<-c('from','to','var24')
colnames(gMatriz_atividade.txt)<-c('from','to','atividade')
colnames(gMatriz_acesso.txt)<-c('from','to','acesso')
colnames(gMatriz_confianca.txt)<-c('from','to','confianca')
colnames(gMatriz_total.txt)<-c('from','to','total')
```

```{r}       
full_data_frame <- cbind(gMatriz_0.txt,
gMatriz_1.txt$var1,
gMatriz_2.txt$var2,
gMatriz_3.txt$var3,
gMatriz_4.txt$var4,
gMatriz_5.txt$var5,
gMatriz_6.txt$var6,
gMatriz_7.txt$var7,
gMatriz_8.txt$var8,
gMatriz_9.txt$var9,
gMatriz_10.txt$var10,
gMatriz_11.txt$var11,
gMatriz_12.txt$var12,
gMatriz_13.txt$var13,
gMatriz_14.txt$var14,
gMatriz_15.txt$var15,
gMatriz_16.txt$var16,
gMatriz_17.txt$var17,
gMatriz_18.txt$var18,
gMatriz_19.txt$var19,
gMatriz_20.txt$var20,
gMatriz_21.txt$var21,
gMatriz_22.txt$var22,
gMatriz_23.txt$var23,
gMatriz_24.txt$var24,
gMatriz_atividade.txt$atividade,
gMatriz_acesso.txt$acesso,
gMatriz_confianca.txt$confianca,
gMatriz_total.txt$total)
head(full_data_frame)
summary(full_data_frame)
head(full_data_frame)

full_data_frame$id<-seq_along(full_data_frame$from)

```

```{r}
names(full_data_frame)[4:31] <- c(
"var1",
"var2",
"var3",
"var4",
"var5",
"var6",
"var7",
"var8",
"var9",
"var10",
"var11",
"var12",
"var13",
"var14",
"var15",
"var16",
"var17",
"var18",
"var19",
"var20",
"var21",
"var22",
"var23",
"var24",
"atividade",
"acesso",
"confianca",
"total")
names(full_data_frame)
```

```{r}
full_nonzero_edges <- subset(full_data_frame, (var0 > 0 |
var1 > 0 |
var2 > 0 |
var3 > 0 |
var4 > 0 |
var5 > 0 |
var6 > 0 |
var7 > 0 |
var8 > 0 |
var9 > 0 |
var10 > 0 |
var11 > 0 |
var12 > 0 |
var13 > 0 |
var14 > 0 |
var15 > 0 |
var16> 0 |
var17 > 0 |
var18 > 0 |
var19 > 0 |
var20 > 0 |
var21 > 0 |
var22 > 0 |
var23 > 0 |
var24 > 0 |
atividade > 0 |
acesso > 0 |
confianca > 0 |
total > 0))

View(full_nonzero_edges)

```

```{r}
#Full with looping and non zero edges
full_zero <- graph.data.frame(full_data_frame) 
summary(full_zero)
```

```{r}
full <- graph.data.frame(full_nonzero_edges, directed = T) 

summary(full)

write.csv2(full_nonzero_edges, "~/full_nonzero_edges.csv", fileEncoding = "macintosh")

write.csv2(attributes.csv, "~/attributes.csv", fileEncoding = "macintosh")

c<-read.table("~/attributos2.csv", fileEncoding = "macintosh", sep = ";")

View(c)


attributes.csv=as.data.frame(attributes.csv)

V(full_zero)$TIPO1=as.character(attributes.csv$TIPO1[match(V(full_zero)$name,attributes.csv$ID)]

attributes.csv$TIPO1

V(net)$name
```

```{r}
#Getting edge attribute example
get.edge.attribute(full)
```

```{r}
full_symmetrized <- as.undirected(full, mode='collapse')
```

```{r}
V(full)
```

```{r}
attributes<-as.data.frame(attributes.csv)
```

```{r}
for (i in V(full_zero)) {
  for (j in names(attributes)) {
    full <- set.vertex.attribute(full_zero, 
                                 j, 
                                 index = i, 
                                 attributes[i, j])
  }
}

attributesx = cbind(1:length(attributes[,1]), attributes)

v<-get.vertex.attribute(full)
v<-as.data.frame(v)
```



```{r}
summary(full)
get.vertex.attribute(full, 'V2_LABEL_ID')
```

```{r}
saveAsGEXF = function(g, filepath="converted_graph.gexf")
  
{
  
  # gexf nodes require two column data frame (id, label)
  
  # check if the input vertices has label already present
  
  # if not, just have the ids themselves as the label
  
  if(is.null(V(g)$label))
    
    V(g)$label <- as.character(V(g)$name)
  
  # similarily if edges does not have weight, add default 1 weight
  
  if(is.null(E(g)$weight))
    
    E(g)$weight <- rep.int(1, ecount(g))
  
  nodes <- data.frame(cbind(V(g), V(g)$label))
  
  edges <- t(Vectorize(get.edge, vectorize.args='id')(g, 1:ecount(g)))
  
  # combine all node attributes into a matrix (and take care of & for xml)
  
  vAttrNames <- setdiff(list.vertex.attributes(g), "label")
  
  nodesAtt <- data.frame(sapply(vAttrNames, function(attr) sub("&", "&",get.vertex.attribute(g, attr))),
                         
                         stringsAsFactors = FALSE)
  
  # combine all edge attributes into a matrix (and take care of & for xml)
  
  eAttrNames <- setdiff(list.edge.attributes(g), "weight")
  
  edgesAtt <- data.frame(sapply(eAttrNames, function(attr) sub("&", "&",get.edge.attribute(g, attr))),
                         
                         stringsAsFactors = FALSE)
  
  # generate the gexf object
  
  output <- write.gexf(nodes, edges,
                       
                       edgesWeight=E(g)$weight,
                       
                       edgesAtt = edgesAtt,
                       
                       nodesAtt = nodesAtt)
  
  print(output, filepath, replace=T)
  
}
```

```{r}
saveAsGEXF(gMatriz_x2.csv, "~/Banco Redes R/Matriz_x2.gexf")
saveAsGEXF(gMatriz_0.csv, "~/Banco Redes R/Matriz_0.gexf")
saveAsGEXF(gMatriz_1.csv, "~/Banco Redes R/Matriz_1.gexf")
saveAsGEXF(gMatriz_2.csv, "~/Banco Redes R/Matriz_2.gexf")
saveAsGEXF(gMatriz_3.csv, "~/Banco Redes R/Matriz_3.gexf")
saveAsGEXF(gMatriz_4.csv, "~/Banco Redes R/Matriz_4.gexf")
saveAsGEXF(gMatriz_5.csv, "~/Banco Redes R/Matriz_5.gexf")
saveAsGEXF(gMatriz_6.csv, "~/Banco Redes R/Matriz_6.gexf")
saveAsGEXF(gMatriz_7.csv, "~/Banco Redes R/Matriz_7.gexf")
saveAsGEXF(gMatriz_8.csv, "~/Banco Redes R/Matriz_8.gexf")
saveAsGEXF(gMatriz_9.csv, "~/Banco Redes R/Matriz_9.gexf")
saveAsGEXF(gMatriz_10.csv, "~/Banco Redes R/Matriz_10.gexf")
saveAsGEXF(gMatriz_11.csv, "~/Banco Redes R/Matriz_11.gexf")
saveAsGEXF(gMatriz_12.csv, "~/Banco Redes R/Matriz_12.gexf")
saveAsGEXF(gMatriz_13.csv, "~/Banco Redes R/Matriz_13.gexf")
saveAsGEXF(gMatriz_14.csv, "~/Banco Redes R/Matriz_14.gexf")
saveAsGEXF(gMatriz_15.csv, "~/Banco Redes R/Matriz_15.gexf")
saveAsGEXF(gMatriz_16.csv, "~/Banco Redes R/Matriz_16.gexf")
saveAsGEXF(gMatriz_17.csv, "~/Banco Redes R/Matriz_17.gexf")
saveAsGEXF(gMatriz_18.csv, "~/Banco Redes R/Matriz_18.gexf")
saveAsGEXF(gMatriz_19.csv, "~/Banco Redes R/Matriz_19.gexf")
saveAsGEXF(gMatriz_20.csv, "~/Banco Redes R/Matriz_20.gexf")
saveAsGEXF(gMatriz_21.csv, "~/Banco Redes R/Matriz_21.gexf")
saveAsGEXF(gMatriz_22.csv, "~/Banco Redes R/Matriz_22.gexf")
saveAsGEXF(gMatriz_23.csv, "~/Banco Redes R/Matriz_23.gexf")
saveAsGEXF(gMatriz_24.csv, "~/Banco Redes R/Matriz_24.gexf")
saveAsGEXF(gMatriz_atividade.csv, "~/Banco Redes R/atividade.gexf")
saveAsGEXF(gMatriz_acesso.csv, "~/Banco Redes R/acesso.gexf")
saveAsGEXF(gMatriz_confianca.csv, "~/Banco Redes R/confianca.gexf")
saveAsGEXF(gMatriz_total.csv, "~/Banco Redes R/total.gexf")
saveAsGEXF(full, "~/Banco Redes R/full.gexf")
```

```{r}
krack_reports_to_only <- delete.edges(full, 
                                      E(full)[get.edge.attribute(full, 
                                                                       name = "var1") == 0])
plot(krack_reports_to_only)

reports_to_layout <- layout.fruchterman.reingold(krack_reports_to_only)

plot(reports_to_layout)

reports_to_layout <- layout.fruchterman.reingold(krack_reports_to_only)
pdf("1.5_Krackhardt_Reports_Fruchterman_Reingold.pdf")
plot(krack_reports_to_only, 
     layout=reports_to_layout)
dev.off()


tenure_vertex_sizes = get.vertex.attribute(full,"total")

pdf("1.7_Krackhardt_Reports_Vertex_Size.pdf") 
plot(krack_reports_to_only, 
     layout=reports_to_layout, 
     vertex.label=NA, 
     edge.arrow.size=.5,
     vertex.size=tenure_vertex_sizes)
dev.off() 




write.graph(full, file='krack_full.txt', format="edgelist")


