---
title: "Banco de Dados Redes"
author: "Leonardo Martins"
date: "17 de maio de 2016"
output: html_document
---

#Calling Packages
```{r packages, message=FALSE, warning=FALSE, include=FALSE}
setwd('~/Banco Redes R')
require(XLConnect)
require(readxl)
require(psych)
require(igraph) #load package for social network analysis
require(networkD3) #load package for sankey network
library(rgexf)
library(reshape2)
suppressMessages(library(igraph))
suppressMessages(library(miniCRAN))
suppressMessages(library(magrittr))
suppressMessages(library(keyplayer))
suppressMessages(library(dplyr))
library(feather)
suppressMessages(library(visNetwork))
library(knitr)
suppressMessages(library(DT))
```


#Open Excel Data Base
```{r functions, , message=FALSE, warning=FALSE, include=FALSE}
# Building read excel allsheets 
read_excel_allsheets <- function(filename) 
{
    sheets <- readxl::excel_sheets(filename)
    x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
    names(x) <- sheets
    x
}
```

## Open each datatable in a different file
```{r opendata, , message=FALSE, warning=FALSE, include=FALSE}
#Creating a list with all spreadsheet
mysheets <- read_excel_allsheets("base.xlsx")
```

## Creating .csv file for each sheet
```{r pressure, message=FALSE, warning=FALSE, include=FALSE}
#Creating each .csv file with mysheets names
for (i in names(mysheets)) 
{
    filename = paste(i, ".csv", sep="")
    write.csv2(mysheets[[i]], filename)
}
```

## Importing Datasets as R Objects (Basic Functions)
```{r , message=FALSE, warning=FALSE, include=FALSE}
#Importing Dataframe

#Importing Matrix (cleaning invalid cases)
importa_matrix <- function(x)
{
x<-as.matrix(assign(x, read.table(x,sep=";", stringsAsFactors=FALSE, header = T, row.names=2)))[-c(70, 105, 109, 126, 131, 133, 154, 166),-c(1,71, 106, 110, 127, 132, 134, 155, 167)]
}


#Importing Matrix (Auxiliary files)
importa_matrix2 <- function(x)
{
x<-as.matrix(assign(x, read.table(x,sep=";", stringsAsFactors=FALSE, header = T)))[,-c(1)]
}


#Importing Matrix (Importing attributes)
importa_matrix3 <- function(x)
{
x<-as.matrix(assign(x, read.table(x,sep=";", stringsAsFactors=FALSE, header = T, row.names=2)))[-c(70, 105, 109, 126, 131, 133, 154, 166),-c(1)]
}

```
#Importing auxiliary data
```{r, message=FALSE, warning=FALSE, include=FALSE}
Casos_Excluidos_Linha_e_Colun.csv<-importa_matrix2("Casos Excluídos - Linha e Colun.csv")
Dicionário_de_dados_choices.csv<-importa_matrix2("Dicionário de dados - choices.csv")
Dicionário_de_dados_survey.csv<-importa_matrix2("Dicionário de dados - survey.csv")
Dicionário_Matrizes.csv<-importa_matrix2("Dicionário Matrizes.csv")
Nó_simplificado_com_GEOCODE.csv<-importa_matrix2("Nó simplificado com GEOCODE.csv")
Nós_Completo.csv<-importa_matrix2("Nós Completo.csv")
Nós_Simplificado.csv<-importa_matrix2("Nós Simplificado.csv")
attributes_dic.csv<-importa_matrix2("Dicionário de dados - atributos.csv")
```

#Importing Squared Matrix
```{r , message=FALSE, warning=FALSE, include=FALSE}

#B1 Tipo de Relacionamento	B1.1 No último ano com quais TIPOS de serviço o SEU SERVIÇO teve alguma relação/ativade em conjunto referente à atenção aos USUÁRIOS DE DROGAS
Matriz_x2.csv<-importa_matrix("Matriz x2.csv")

#B1 Tipo de Relacionamento	B1.2 – TIPOS DE RELACIONAMENTO - FORMAL. No que se refere à ATENÇÃO aos USUÁRIOS DE DROGAS, você caracteriza como FORMAL o relacionamento que o seu serviço possui com os #serviços a seguir ? Parceria Formal - Feita através de paceria/fluxo institucional devadmente reconheca, por meio de convênios, contratos, ou acordo entre gesotres/secretarias etc.
Matriz_0.csv<-importa_matrix("Matriz 0.csv")

#B2- ATIVADES EM CONJUNTO	B2.1 – TIPOS DE RELACIONAMENTO - REFERENCIA DE ENVIO  - O SEU SERVIÇO MANTÉM ALGUM TIPO DE REFERÊNCIA DE ENVIO OU ENCAMINHAMENTO DE USUÁRIO DE DROGAS COM OS SERVIÇOS A SEGUIR: #REFERENCIA DE ENVIO - Usuários de Drogas encaminhados a outros serviços da rede
Matriz_1.csv<-importa_matrix("Matriz 1.csv")

#B2- ATIVADES EM CONJUNTO	B2.2 – TIPOS DE RELACIONAMENTO - REFERENCIA DE RECEBIMENTO CONTRAREFERENCIA - O SEU SERVIÇO MANTÉM ALGUM TIPO DE REFERÊNCIA DE RECEBIMENTO OU CONTRAREFERENCIA DE USUÁRIO DE #DROGAS COM: REFERENCIA DE RECEBIMENTO CONTRAREFERENCIA  - USUÁRIOS DE DROGAS RECEBOS OU CONTRAREFERENCIADOS DE OUTROS SERVIÇOS DA REDE
Matriz_2.csv<-importa_matrix("Matriz 2.csv")

#B2- ATIVADES EM CONJUNTO	B2.3 – TIPOS DE RELACIONAMENTO  - COORDENAÇÃO CONJUNTA DE CASOS  - O SEU SERVIÇO MANTÉM ALGUM TIPO DE COORDENAÇÃO CONJUNTA DE CASOS REFERENTE AO USO DE DROGAS COM: COORDENAÇÃO #CONJUNTA DE CASOS - COMPARTILHAMENTO DE DADOS E CONDUTAS A RESPEITO DE UM CASO ESPECÍFICO RELACIONADO AO USO DE DROGAS, RESPONSABILADE COMPARTILHADA DE CASOS, TRATAMENTO DE USUÁRIOS DE DROGAS EM CONJUNTO #COM OUTROS SERVIÇOS
Matriz_3.csv<-importa_matrix("Matriz 3.csv")

#B2- ATIVADES EM CONJUNTO	B2.4 – TIPOS DE RELACIONAMENTO - PROGRAMAS EM CONJUNTO - O SEU SERVIÇO MANTÉM ALGUM TIPO DE PROGRAMA EM CONJUNTO REFERENTE AO USO DE DROGAS COM: PROGRAMAS EM CONJUNTO  - #PROGRAMAS E PROJETOS REFERENTES AO USO DE DROGAS DESENVOLVOS EM CONJUNTO COM OUTROS SERVIÇOS
Matriz_4.csv<-importa_matrix("Matriz 4.csv")

#B2- ATIVADES EM CONJUNTO	B2.5 – TIPOS DE RELACIONAMENTO  - OFERTA DE TREINAMENTOS/CAPACITAÇÕES - COM RELAÇÃO AO USO DE DROGAS, O SEU SERVIÇO JÁ TREINOU OU CAPACITOU ALGUM DOS SERVIÇOS A SEGUIR:  OFERTA #DE TREINAMENTOS/CAPACITAÇÕES  - CURSOS CAPACITAÇÕES TREINAMENTOS OU OUTROS EVENTOS DE EDUCAÇÃO PERMANENTE RELACIONADOS AO USO DE DROGAS OFERECOS PARA OUTROS SERVIÇOS PARA MELHORIA DA QUALIFICAÇÃO #PROFISSIONAL
Matriz_5.csv<-importa_matrix("Matriz 5.csv")

#B2- ATIVADES EM CONJUNTO	B2.6 – TIPOS DE RELACIONAMENTO  - RECEBER TREINAMENTOS/CAPACITAÇÕES - COM RELAÇÃO AO USO DE DROGAS, O SEU SERVIÇO JÁ FOI TREINADO OU CAPACITADO POR ALGUM DOS SERVIÇOS A SEGUIR: #RECEBER TREINAMENTOS/CAPACITAÇÕES - CURSOS CAPACITAÇÕES TREINAMENTOS OU OUTROS EVENTOS DE EDUCAÇÃO PERMANENTE REFERENTES AO USO DE DROGAS RECEBOS DE OUTROS SERVIÇOS PARA MELHORIA DA QUALIFICAÇÃO #PROFISSIONAL 
Matriz_6.csv<-importa_matrix("Matriz 6.csv")

#ACESSO	A) Este serviço mostra-se disponível para realização de ativades em conjunto.
Matriz_7.csv<-importa_matrix("Matriz 7.csv")

#ACESSO	B) O horário de funcionamento deste serviço possibilita a realização de ações em conjunto.
Matriz_8.csv<-importa_matrix("Matriz 8.csv")

#ACESSO	C) Este serviço disponibiliza informações sobre suas ativades para o seu serviço.
Matriz_9.csv<-importa_matrix("Matriz 9.csv")

#ACESSO	D) O seu serviço consegue acessar facilmente informações deste serviço.
Matriz_10.csv<-importa_matrix("Matriz 10.csv")

#ACESSO	E) Os canais de comunicação com este serviço são suficientes para realização de ações em conjunto.
Matriz_11.csv<-importa_matrix("Matriz 11.csv")

#CONFIANÇA	I) Seu serviço espera que o relacionamento com este serviço se fortaleça nos próximos anos.
Matriz_12.csv<-importa_matrix("Matriz 12.csv")


#ACESSO	F) Seu serviço tem facilade de entrar em contato com este serviço para realizar ativades em conjunto.
Matriz_13.csv<-importa_matrix("Matriz 13.csv")


#ACESSO	G) O acesso geográfico a este serviço impede a realização de ativades em conjunto.  
Matriz_14.csv<-importa_matrix("Matriz 14.csv")


#ACESSO	H) O custo para acessar este serviço impede a realização de ativades em conjunto.
Matriz_15.csv<-importa_matrix("Matriz 15.csv")


#ACESSO	I) O tempo gasto para acessar este serviço impede a realização ativades em conjunto.
Matriz_16.csv<-importa_matrix("Matriz 16.csv")


#CONFIANÇA	A) Seu serviço confia  na qualificação profissional da equipe deste serviço 
Matriz_17.csv<-importa_matrix("Matriz 17.csv")

#CONFIANÇA	B) Seu serviço confia  na capacade técnica da equipe deste serviço.
Matriz_18.csv<-importa_matrix("Matriz 18.csv")


#CONFIANÇA	C) Seu serviço confia  nas ações realizadas por este serviço.
Matriz_19.csv<-importa_matrix("Matriz 19.csv")


#CONFIANÇA	D) Seu serviço confia  em compartilhar informações internas com este serviço. 
Matriz_20.csv<-importa_matrix("Matriz 20.csv")


#CONFIANÇA	E) Seu serviço confia nas informações recebas deste serviço.
Matriz_21.csv<-importa_matrix("Matriz 21.csv")


#CONFIANÇA	F) Seu serviço confia  em realizar ações conjuntas com este serviço.
Matriz_22.csv<-importa_matrix("Matriz 22.csv")


#CONFIANÇA	G) Seu serviço está satisfeito  com as ações desempenhadas por este serviço.
Matriz_23.csv<-importa_matrix("Matriz 23.csv")


#CONFIANÇA	H) Seu serviço espera que o relacionamento com este serviço continue nos próximos anos.
Matriz_24.csv<-importa_matrix("Matriz 24.csv")

#SOMATÓRIO ATIVIDADE
atividade= as.matrix(`Matriz_1.csv` + `Matriz_2.csv` + `Matriz_3.csv` + `Matriz_4.csv`+ `Matriz_5.csv`+ `Matriz_6.csv`)

#SOMATÓRIO ACESSO
acesso= as.matrix(`Matriz_7.csv` + `Matriz_8.csv` + `Matriz_9.csv` + `Matriz_10.csv`+ `Matriz_11.csv`+ `Matriz_12.csv` + `Matriz_13.csv` + `Matriz_14.csv` + `Matriz_15.csv` + `Matriz_16.csv`)

#SOMATÓRIO CONFIANÇA
confianca=as.matrix(`Matriz_17.csv` + `Matriz_18.csv` + `Matriz_19.csv` + `Matriz_20.csv` + `Matriz_21.csv` + `Matriz_22.csv` + `Matriz_23.csv` + `Matriz_24.csv`)

#SOMATÓRIO TOTAL
total= as.matrix(atividade + acesso + confianca)
```


#Importing Attributes for vertices
```{r , message=FALSE, warning=FALSE, include=FALSE}
attributes.csv<-as.data.frame(importa_matrix3("Atributos.csv"))
attributes.csv$V3_LABEL_ID2=as.character(attributes.csv$V3_LABEL_ID2)
attributes.csv$V3_LABEL_ID2=as.numeric(attributes.csv$V3_LABEL_ID2)
```

#Genenating Igrah Objects
```{r, message=FALSE, warning=FALSE, include=FALSE}
gMatriz_x2.csv<-graph_from_adjacency_matrix(Matriz_x2.csv, mode="directed",weighted=T,diag=F)
gMatriz_0.csv<-graph_from_adjacency_matrix(Matriz_0.csv, mode="directed",weighted=T,diag=F)
gMatriz_1.csv<-graph_from_adjacency_matrix(Matriz_1.csv, mode="directed",weighted=T,diag=F)
gMatriz_2.csv<-graph_from_adjacency_matrix(Matriz_2.csv, mode="directed",weighted=T,diag=F)
gMatriz_3.csv<-graph_from_adjacency_matrix(Matriz_3.csv, mode="directed",weighted=T,diag=F)
gMatriz_4.csv<-graph_from_adjacency_matrix(Matriz_4.csv, mode="directed",weighted=T,diag=F)
gMatriz_5.csv<-graph_from_adjacency_matrix(Matriz_5.csv, mode="directed",weighted=T,diag=F)
gMatriz_6.csv<-graph_from_adjacency_matrix(Matriz_6.csv, mode="directed",weighted=T,diag=F)
gMatriz_7.csv<-graph_from_adjacency_matrix(Matriz_7.csv, mode="directed",weighted=T,diag=F)
gMatriz_8.csv<-graph_from_adjacency_matrix(Matriz_8.csv, mode="directed",weighted=T,diag=F)
gMatriz_9.csv<-graph_from_adjacency_matrix(Matriz_9.csv, mode="directed",weighted=T,diag=F)
gMatriz_10.csv<-graph_from_adjacency_matrix(Matriz_10.csv, mode="directed",weighted=T,diag=F)
gMatriz_11.csv<-graph_from_adjacency_matrix(Matriz_11.csv, mode="directed",weighted=T,diag=F)
gMatriz_12.csv<-graph_from_adjacency_matrix(Matriz_12.csv, mode="directed",weighted=T,diag=F)
gMatriz_13.csv<-graph_from_adjacency_matrix(Matriz_13.csv, mode="directed",weighted=T,diag=F)
gMatriz_14.csv<-graph_from_adjacency_matrix(Matriz_14.csv, mode="directed",weighted=T,diag=F)
gMatriz_15.csv<-graph_from_adjacency_matrix(Matriz_15.csv, mode="directed",weighted=T,diag=F)
gMatriz_16.csv<-graph_from_adjacency_matrix(Matriz_16.csv, mode="directed",weighted=T,diag=F)
gMatriz_17.csv<-graph_from_adjacency_matrix(Matriz_17.csv, mode="directed",weighted=T,diag=F)
gMatriz_18.csv<-graph_from_adjacency_matrix(Matriz_18.csv, mode="directed",weighted=T,diag=F)
gMatriz_19.csv<-graph_from_adjacency_matrix(Matriz_19.csv, mode="directed",weighted=T,diag=F)
gMatriz_20.csv<-graph_from_adjacency_matrix(Matriz_20.csv, mode="directed",weighted=T,diag=F)
gMatriz_21.csv<-graph_from_adjacency_matrix(Matriz_21.csv, mode="directed",weighted=T,diag=F)
gMatriz_22.csv<-graph_from_adjacency_matrix(Matriz_22.csv, mode="directed",weighted=T,diag=F)
gMatriz_23.csv<-graph_from_adjacency_matrix(Matriz_23.csv, mode="directed",weighted=T,diag=F)
gMatriz_24.csv<-graph_from_adjacency_matrix(Matriz_24.csv, mode="directed",weighted=T,diag=F)
gMatriz_atividade.csv<-graph_from_adjacency_matrix(atividade, mode="directed",weighted=T,diag=F)
gMatriz_acesso.csv<-graph_from_adjacency_matrix(acesso, mode="directed",weighted=T,diag=F)
gMatriz_confianca.csv<-graph_from_adjacency_matrix(confianca, mode="directed",weighted=T,diag=F)
gMatriz_total.csv<-graph_from_adjacency_matrix(total, mode="directed",weighted=T,diag=F)
```

#GEXF Function to export igraph objects to Gephi 
```{r , message=FALSE, warning=FALSE, include=FALSE}
saveAsGEXF = function(g, filepath="converted_graph.gexf")
  
{
  
  # gexf nodes require two column data frame (id, label)
  
  # check if the input vertices has label already present
  
  # if not, just have the ids themselves as the label
  
  if(is.null(V(g)$label))
    
    V(g)$label <- as.character(V(g)$name)
  
  # similarily if edges does not have weight, add default 1 weight
  
  if(is.null(E(g)$weight))
    
    E(g)$weight <- rep.int(1, ecount(g))
  
  nodes <- data.frame(cbind(V(g), V(g)$label))
  
  edges <- t(Vectorize(get.edge, vectorize.args='id')(g, 1:ecount(g)))
  
  # combine all node attributes into a matrix (and take care of & for xml)
  
  vAttrNames <- setdiff(list.vertex.attributes(g), "label")
  
  nodesAtt <- data.frame(sapply(vAttrNames, function(attr) sub("&", "&",get.vertex.attribute(g, attr))),
                         
                         stringsAsFactors = FALSE)
  
  # combine all edge attributes into a matrix (and take care of & for xml)
  
  eAttrNames <- setdiff(list.edge.attributes(g), "weight")
  
  edgesAtt <- data.frame(sapply(eAttrNames, function(attr) sub("&", "&",get.edge.attribute(g, attr))),
                         
                         stringsAsFactors = FALSE)
  
  # generate the gexf object
  
  output <- write.gexf(nodes, edges,
                       
                       edgesWeight=E(g)$weight,
                       
                       edgesAtt = edgesAtt,
                       
                       nodesAtt = nodesAtt)
  
  print(output, filepath, replace=T)
  
}
```

#Exporting Gexf objects to Banco Redes R
```{r, message=FALSE, warning=FALSE, include=FALSE}
saveAsGEXF(gMatriz_x2.csv, "~/Banco Redes R/Matriz_x2.gexf")
saveAsGEXF(gMatriz_0.csv, "~/Banco Redes R/Matriz_0.gexf")
saveAsGEXF(gMatriz_1.csv, "~/Banco Redes R/Matriz_1.gexf")
saveAsGEXF(gMatriz_2.csv, "~/Banco Redes R/Matriz_2.gexf")
saveAsGEXF(gMatriz_3.csv, "~/Banco Redes R/Matriz_3.gexf")
saveAsGEXF(gMatriz_4.csv, "~/Banco Redes R/Matriz_4.gexf")
saveAsGEXF(gMatriz_5.csv, "~/Banco Redes R/Matriz_5.gexf")
saveAsGEXF(gMatriz_6.csv, "~/Banco Redes R/Matriz_6.gexf")
saveAsGEXF(gMatriz_7.csv, "~/Banco Redes R/Matriz_7.gexf")
saveAsGEXF(gMatriz_8.csv, "~/Banco Redes R/Matriz_8.gexf")
saveAsGEXF(gMatriz_9.csv, "~/Banco Redes R/Matriz_9.gexf")
saveAsGEXF(gMatriz_10.csv, "~/Banco Redes R/Matriz_10.gexf")
saveAsGEXF(gMatriz_11.csv, "~/Banco Redes R/Matriz_11.gexf")
saveAsGEXF(gMatriz_12.csv, "~/Banco Redes R/Matriz_12.gexf")
saveAsGEXF(gMatriz_13.csv, "~/Banco Redes R/Matriz_13.gexf")
saveAsGEXF(gMatriz_14.csv, "~/Banco Redes R/Matriz_14.gexf")
saveAsGEXF(gMatriz_15.csv, "~/Banco Redes R/Matriz_15.gexf")
saveAsGEXF(gMatriz_16.csv, "~/Banco Redes R/Matriz_16.gexf")
saveAsGEXF(gMatriz_17.csv, "~/Banco Redes R/Matriz_17.gexf")
saveAsGEXF(gMatriz_18.csv, "~/Banco Redes R/Matriz_18.gexf")
saveAsGEXF(gMatriz_19.csv, "~/Banco Redes R/Matriz_19.gexf")
saveAsGEXF(gMatriz_20.csv, "~/Banco Redes R/Matriz_20.gexf")
saveAsGEXF(gMatriz_21.csv, "~/Banco Redes R/Matriz_21.gexf")
saveAsGEXF(gMatriz_22.csv, "~/Banco Redes R/Matriz_22.gexf")
saveAsGEXF(gMatriz_23.csv, "~/Banco Redes R/Matriz_23.gexf")
saveAsGEXF(gMatriz_24.csv, "~/Banco Redes R/Matriz_24.gexf")
saveAsGEXF(gMatriz_atividade.csv, "~/Banco Redes R/atividade.gexf")
saveAsGEXF(gMatriz_acesso.csv, "~/Banco Redes R/acesso.gexf")
saveAsGEXF(gMatriz_confianca.csv, "~/Banco Redes R/confianca.gexf")
saveAsGEXF(gMatriz_total.csv, "~/Banco Redes R/total.gexf")
```


#Melting Squared Matrix to List in order to agreggate all lists in one dataframe
```{r, message=FALSE, warning=FALSE, include=FALSE}
gMatriz_x2.txt<-melt(Matriz_x2.csv)
gMatriz_0.txt<-melt(Matriz_0.csv)
gMatriz_1.txt<-melt(Matriz_1.csv)
gMatriz_2.txt<-melt(Matriz_2.csv)
gMatriz_3.txt<-melt(Matriz_3.csv)
gMatriz_4.txt<-melt(Matriz_4.csv)
gMatriz_5.txt<-melt(Matriz_5.csv)
gMatriz_6.txt<-melt(Matriz_6.csv)
gMatriz_7.txt<-melt(Matriz_7.csv)
gMatriz_8.txt<-melt(Matriz_8.csv)
gMatriz_9.txt<-melt(Matriz_9.csv)
gMatriz_10.txt<-melt(Matriz_10.csv)
gMatriz_11.txt<-melt(Matriz_11.csv)
gMatriz_12.txt<-melt(Matriz_12.csv)
gMatriz_13.txt<-melt(Matriz_13.csv)
gMatriz_14.txt<-melt(Matriz_14.csv)
gMatriz_15.txt<-melt(Matriz_15.csv)
gMatriz_16.txt<-melt(Matriz_16.csv)
gMatriz_17.txt<-melt(Matriz_17.csv)
gMatriz_18.txt<-melt(Matriz_18.csv)
gMatriz_19.txt<-melt(Matriz_19.csv)
gMatriz_20.txt<-melt(Matriz_20.csv)
gMatriz_21.txt<-melt(Matriz_21.csv)
gMatriz_22.txt<-melt(Matriz_22.csv)
gMatriz_23.txt<-melt(Matriz_23.csv)
gMatriz_24.txt<-melt(Matriz_24.csv)
gMatriz_atividade.txt<-melt(atividade)
gMatriz_acesso.txt<-melt(acesso)
gMatriz_confianca.txt<-melt(confianca)
gMatriz_total.txt<-melt(total)
```

#Adding colnames
```{r, message=FALSE, warning=FALSE, include=FALSE}
colnames(gMatriz_x2.txt)<-c('from','to','x2')
colnames(gMatriz_0.txt)<-c('from','to','var0')
colnames(gMatriz_1.txt)<-c('from','to','var1')
colnames(gMatriz_2.txt)<-c('from','to','var2')
colnames(gMatriz_3.txt)<-c('from','to','var3')
colnames(gMatriz_4.txt)<-c('from','to','var4')
colnames(gMatriz_5.txt)<-c('from','to','var5')
colnames(gMatriz_6.txt)<-c('from','to','var6')
colnames(gMatriz_7.txt)<-c('from','to','var7')
colnames(gMatriz_8.txt)<-c('from','to','var8')
colnames(gMatriz_9.txt)<-c('from','to','var9')
colnames(gMatriz_10.txt)<-c('from','to','var10')
colnames(gMatriz_11.txt)<-c('from','to','var11')
colnames(gMatriz_12.txt)<-c('from','to','var12')
colnames(gMatriz_13.txt)<-c('from','to','var13')
colnames(gMatriz_14.txt)<-c('from','to','var14')
colnames(gMatriz_15.txt)<-c('from','to','var15')
colnames(gMatriz_16.txt)<-c('from','to','var16')
colnames(gMatriz_17.txt)<-c('from','to','var17')
colnames(gMatriz_18.txt)<-c('from','to','var18')
colnames(gMatriz_19.txt)<-c('from','to','var19')
colnames(gMatriz_20.txt)<-c('from','to','var20')
colnames(gMatriz_21.txt)<-c('from','to','var21')
colnames(gMatriz_22.txt)<-c('from','to','var22')
colnames(gMatriz_23.txt)<-c('from','to','var23')
colnames(gMatriz_24.txt)<-c('from','to','var24')
colnames(gMatriz_atividade.txt)<-c('from','to','atividade')
colnames(gMatriz_acesso.txt)<-c('from','to','acesso')
colnames(gMatriz_confianca.txt)<-c('from','to','confianca')
colnames(gMatriz_total.txt)<-c('from','to','total')
```

#All matrixes in one dataframe
```{r, message=FALSE, warning=FALSE, include=FALSE}       
full_data_frame <- cbind(gMatriz_0.txt,
gMatriz_1.txt$var1,
gMatriz_2.txt$var2,
gMatriz_3.txt$var3,
gMatriz_4.txt$var4,
gMatriz_5.txt$var5,
gMatriz_6.txt$var6,
gMatriz_7.txt$var7,
gMatriz_8.txt$var8,
gMatriz_9.txt$var9,
gMatriz_10.txt$var10,
gMatriz_11.txt$var11,
gMatriz_12.txt$var12,
gMatriz_13.txt$var13,
gMatriz_14.txt$var14,
gMatriz_15.txt$var15,
gMatriz_16.txt$var16,
gMatriz_17.txt$var17,
gMatriz_18.txt$var18,
gMatriz_19.txt$var19,
gMatriz_20.txt$var20,
gMatriz_21.txt$var21,
gMatriz_22.txt$var22,
gMatriz_23.txt$var23,
gMatriz_24.txt$var24,
gMatriz_atividade.txt$atividade,
gMatriz_acesso.txt$acesso,
gMatriz_confianca.txt$confianca,
gMatriz_total.txt$total)
head(full_data_frame)
```

#Renaming 
```{r, message=FALSE, warning=FALSE, include=FALSE}
names(full_data_frame)[4:31] <- c(
"var1",
"var2",
"var3",
"var4",
"var5",
"var6",
"var7",
"var8",
"var9",
"var10",
"var11",
"var12",
"var13",
"var14",
"var15",
"var16",
"var17",
"var18",
"var19",
"var20",
"var21",
"var22",
"var23",
"var24",
"atividade",
"acesso",
"confianca",
"total")
names(full_data_frame)

#Writing file to excel 
write.csv2(full_data_frame, "~/Banco Redes R/full_data_frame.csv", fileEncoding = "macintosh")

#Changing ID to number on Excel (ps: improve this code using R)
full_data_frame_id=read.table("~/Banco Redes R/full_data_frame_id.csv", sep=";", stringsAsFactors=FALSE, header = T)

#Changing types for futher matching
full_data_frame_id$from<-as.character(full_data_frame_id$from)
full_data_frame_id$from<-as.numeric(full_data_frame_id$from)
full_data_frame_id$to<-as.character(full_data_frame_id$to)
full_data_frame_id$to<-as.numeric(full_data_frame_id$to)

#Full igrpah object with looping and non zero edges
full_with_zero <- graph_from_data_frame(full_data_frame_id, directed=T) 
V(full_with_zero)$name<-as.character(V(full_with_zero)$name)
V(full_with_zero)$name<-as.numeric(V(full_with_zero)$name)
#full_with_zero<-full_with_zero[order(V(full_with_zero)$name),]
summary(full_with_zero)
```

#Creating non zero dataframe (excluding ties with weight > 0)
```{r, message=FALSE, warning=FALSE, include=FALSE}
full_nonzero_edges <- subset(full_data_frame_id, (var0 > 0 |
var1 > 0 |
var2 > 0 |
var3 > 0 |
var4 > 0 |
var5 > 0 |
var6 > 0 |
var7 > 0 |
var8 > 0 |
var9 > 0 |
var10 > 0 |
var11 > 0 |
var12 > 0 |
var13 > 0 |
var14 > 0 |
var15 > 0 |
var16> 0 |
var17 > 0 |
var18 > 0 |
var19 > 0 |
var20 > 0 |
var21 > 0 |
var22 > 0 |
var23 > 0 |
var24 > 0 |
atividade > 0 |
acesso > 0 |
confianca > 0 |
total > 0))
head(full_nonzero_edges)

#Write DataFrame in order to use with pajek (just in case)
write.csv2(full_nonzero_edges, "~/Banco Redes R/full_nonzero_edges.csv", fileEncoding = "macintosh")

#To be sure - from and to (id's) as numeric
full_nonzero_edges$from<-as.numeric(full_nonzero_edges$from)
full_nonzero_edges$to<-as.numeric(full_nonzero_edges$to)

#Sorting by from - considering previous problems with matching 
full_nonzero_edges=full_nonzero_edges[order(full_nonzero_edges$from),]
head(full_nonzero_edges)

#Full igraph object without looping or zero edges
full_no_zero <- graph_from_data_frame(full_nonzero_edges, directed=T) 
V(full_no_zero)$name<-as.character(V(full_no_zero)$name)
V(full_no_zero)$name<-as.numeric(V(full_no_zero)$name)
summary(full_no_zero)

#Sorting in order to prevent disasters 
V(full_no_zero)$name=sort(as.numeric(V(full_no_zero)$name))
V(full_no_zero)$name
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
# The coolest part - adding attributes to each node (full_with_zero) - Update this code with "for" and after Pedro's updates regarding KML mercartor coordinates 
V(full_with_zero)$ID=as.character(attributes.csv$ID[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$TIPO1=as.character(attributes.csv$TIPO1[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$TIPO2=as.character(attributes.csv$TIPO2[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V1_LABEL_TIPO=as.character(attributes.csv$V1_LABEL_TIPO[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V2_LABEL_ID=as.character(attributes.csv$V2_LABEL_ID[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V3_LABEL_ID2=as.character(attributes.csv$V3_LABEL_ID2[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V4_LABEL_ID3=as.character(attributes.csv$V4_LABEL_ID3[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V5_LABEL_LABEL=as.character(attributes.csv$V5_LABEL_LABEL[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V6_COMUNICACAO_Dispõe.de.meios.de.comunicação=as.character(attributes.csv$V6_COMUNICACAO_Dispõe.de.meios.de.comunicação[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V7_COMUNICACAO_Telefeno.Fixo=as.character(attributes.csv$V7_COMUNICACAO_Telefeno.Fixo[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V8_COMUNICACAO_Celular.Chamada.de.Voz=as.character(attributes.csv$V8_COMUNICACAO_Celular.Chamada.de.Voz[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V9_COMUNICACAO_Celular.Mensagem.de.Texto=as.character(attributes.csv$V9_COMUNICACAO_Celular.Mensagem.de.Texto[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V10_COMUNICACAO_E.mail=as.character(attributes.csv$V10_COMUNICACAO_E.mail[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V11_COMUNICACAO_Skype.Menssager=as.character(attributes.csv$V11_COMUNICACAO_Skype.Menssager[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V12_COMUNICACAO_Converso.Pessalmente=as.character(attributes.csv$V12_COMUNICACAO_Converso.Pessalmente[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V13_COMUNICACAO_Comunicação.Institucional..Ofício..Memorando.=as.character(attributes.csv$V13_COMUNICACAO_Comunicação.Institucional..Ofício..Memorando.[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V14_COMUNICACAO_Outro=as.character(attributes.csv$V14_COMUNICACAO_Outro[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V15_COMUNICACAO_FACEBOOK.REDES.SOCAIS=as.character(attributes.csv$V15_COMUNICACAO_FACEBOOK.REDES.SOCAIS[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V16_TEMPO_FUNC_Data_Abertura=as.character(attributes.csv$V16_TEMPO_FUNC_Data_Abertura[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V17_TEMPO_FUNC_Data_Pesquisa=as.character(attributes.csv$V17_TEMPO_FUNC_Data_Pesquisa[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V18_TEMPO_FUNC_Idade_Serviço_Dias=as.character(attributes.csv$V18_TEMPO_FUNC_Idade_Serviço_Dias[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V19_TEMPO_FUNC_Idade_em_anos=as.character(attributes.csv$V19_TEMPO_FUNC_Idade_em_anos[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V20_FUNCIONAMENTO_Segunda=as.character(attributes.csv$V20_FUNCIONAMENTO_Segunda[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V21_FUNCIONAMENTO_Terça=as.character(attributes.csv$V21_FUNCIONAMENTO_Terça[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V22_FUNCIONAMENTO_Quarta=as.character(attributes.csv$V22_FUNCIONAMENTO_Quarta[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V23_FUNCIONAMENTO_Quinta=as.character(attributes.csv$V23_FUNCIONAMENTO_Quinta[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V24_FUNCIONAMENTO_Sexta=as.character(attributes.csv$V24_FUNCIONAMENTO_Sexta[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V25_FUNCIONAMENTO_Sábado=as.character(attributes.csv$V25_FUNCIONAMENTO_Sábado[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V26_FUNCIONAMENTO_Domingo=as.character(attributes.csv$V26_FUNCIONAMENTO_Domingo[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V27_FUNCIONAMENTO_Feriados=as.character(attributes.csv$V27_FUNCIONAMENTO_Feriados[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V28_FUNCIONAMENTO_Segunda....Manhã=as.character(attributes.csv$V28_FUNCIONAMENTO_Segunda....Manhã[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V29_FUNCIONAMENTO_Segunda....Tarde=as.character(attributes.csv$V29_FUNCIONAMENTO_Segunda....Tarde[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V30_FUNCIONAMENTO_Segunda....Noite=as.character(attributes.csv$V30_FUNCIONAMENTO_Segunda....Noite[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V31_FUNCIONAMENTO_Segunda....Plantão.24h=as.character(attributes.csv$V31_FUNCIONAMENTO_Segunda....Plantão.24h[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V32_FUNCIONAMENTO_Terça....Manhã=as.character(attributes.csv$V32_FUNCIONAMENTO_Terça....Manhã[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V33_FUNCIONAMENTO_Terça....Tarde=as.character(attributes.csv$V33_FUNCIONAMENTO_Terça....Tarde[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V34_FUNCIONAMENTO_Terça....Noite=as.character(attributes.csv$V34_FUNCIONAMENTO_Terça....Noite[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V35_FUNCIONAMENTO_Terça....Plantão.24h=as.character(attributes.csv$V35_FUNCIONAMENTO_Terça....Plantão.24h[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V36_FUNCIONAMENTO_Quarta....Manhã=as.character(attributes.csv$V36_FUNCIONAMENTO_Quarta....Manhã[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V37_FUNCIONAMENTO_Quarta....Tarde=as.character(attributes.csv$V37_FUNCIONAMENTO_Quarta....Tarde[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V38_FUNCIONAMENTO_Quarta....Noite=as.character(attributes.csv$V38_FUNCIONAMENTO_Quarta....Noite[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V39_FUNCIONAMENTO_Quarta....Plantão.24h=as.character(attributes.csv$V39_FUNCIONAMENTO_Quarta....Plantão.24h[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V40_FUNCIONAMENTO_Quinta....Manhã=as.character(attributes.csv$V40_FUNCIONAMENTO_Quinta....Manhã[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V41_FUNCIONAMENTO_Quinta....Tarde=as.character(attributes.csv$V41_FUNCIONAMENTO_Quinta....Tarde[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V42_FUNCIONAMENTO_Quinta....Noite=as.character(attributes.csv$V42_FUNCIONAMENTO_Quinta....Noite[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V43_FUNCIONAMENTO_Quinta....Plantão.24h=as.character(attributes.csv$V43_FUNCIONAMENTO_Quinta....Plantão.24h[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V44_FUNCIONAMENTO_Sexta....Manhã=as.character(attributes.csv$V44_FUNCIONAMENTO_Sexta....Manhã[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V45_FUNCIONAMENTO_Sexta....Tarde=as.character(attributes.csv$V45_FUNCIONAMENTO_Sexta....Tarde[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V46_FUNCIONAMENTO_Sexta....Noite=as.character(attributes.csv$V46_FUNCIONAMENTO_Sexta....Noite[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V47_FUNCIONAMENTO_Sexta....Plantão.24h=as.character(attributes.csv$V47_FUNCIONAMENTO_Sexta....Plantão.24h[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V48_FUNCIONAMENTO_Sábado....Manhã=as.character(attributes.csv$V48_FUNCIONAMENTO_Sábado....Manhã[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V49_FUNCIONAMENTO_Sábado....Tarde=as.character(attributes.csv$V49_FUNCIONAMENTO_Sábado....Tarde[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V50_FUNCIONAMENTO_Sábado....Noite=as.character(attributes.csv$V50_FUNCIONAMENTO_Sábado....Noite[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V51_FUNCIONAMENTO_Sábado....Plantão.24h=as.character(attributes.csv$V51_FUNCIONAMENTO_Sábado....Plantão.24h[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V52_FUNCIONAMENTO_Domingo....Manhã=as.character(attributes.csv$V52_FUNCIONAMENTO_Domingo....Manhã[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V53_FUNCIONAMENTO_Domingo....Tarde=as.character(attributes.csv$V53_FUNCIONAMENTO_Domingo....Tarde[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V54_FUNCIONAMENTO_Domingo....Noite=as.character(attributes.csv$V54_FUNCIONAMENTO_Domingo....Noite[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V55_FUNCIONAMENTO_Domingo....Plantão.24h=as.character(attributes.csv$V55_FUNCIONAMENTO_Domingo....Plantão.24h[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V56_FUNCIONAMENTO_Feriado....Manhã=as.character(attributes.csv$V56_FUNCIONAMENTO_Feriado....Manhã[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V57_FUNCIONAMENTO_Feriado....Tarde=as.character(attributes.csv$V57_FUNCIONAMENTO_Feriado....Tarde[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V58_FUNCIONAMENTO_Feriado....Noite=as.character(attributes.csv$V58_FUNCIONAMENTO_Feriado....Noite[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V59_FUNCIONAMENTO_Feriado....Plantão.24h=as.character(attributes.csv$V59_FUNCIONAMENTO_Feriado....Plantão.24h[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V60_PROFISSIONAIS_Agentes.Comunitários.de.Saúde=as.character(attributes.csv$V60_PROFISSIONAIS_Agentes.Comunitários.de.Saúde[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V61_PROFISSIONAIS_Assistentes.Sociais=as.character(attributes.csv$V61_PROFISSIONAIS_Assistentes.Sociais[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V62_PROFISSIONAIS_Auxiliares.de.Enfermagem=as.character(attributes.csv$V62_PROFISSIONAIS_Auxiliares.de.Enfermagem[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V63_PROFISSIONAIS_Enfermeiros=as.character(attributes.csv$V63_PROFISSIONAIS_Enfermeiros[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V64_PROFISSIONAIS_Auxiliares.de.Consultório.Bucal=as.character(attributes.csv$V64_PROFISSIONAIS_Auxiliares.de.Consultório.Bucal[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V65_PROFISSIONAIS_Médicos=as.character(attributes.csv$V65_PROFISSIONAIS_Médicos[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V66_PROFISSIONAIS_Psicólogos=as.character(attributes.csv$V66_PROFISSIONAIS_Psicólogos[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V67_PROFISSIONAIS_Fisioterapeutas=as.character(attributes.csv$V67_PROFISSIONAIS_Fisioterapeutas[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V68_PROFISSIONAIS_Terapeutas.Ocupacionais=as.character(attributes.csv$V68_PROFISSIONAIS_Terapeutas.Ocupacionais[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V69_PROFISSIONAIS_Dentistas=as.character(attributes.csv$V69_PROFISSIONAIS_Dentistas[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V70_PROFISSIONAIS_Farmacêuticos=as.character(attributes.csv$V70_PROFISSIONAIS_Farmacêuticos[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V71_PROFISSIONAIS_Administradores=as.character(attributes.csv$V71_PROFISSIONAIS_Administradores[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V72_PROFISSIONAIS_Agentes.de.segurança..guardas..rondas.vigilantes.=as.character(attributes.csv$V72_PROFISSIONAIS_Agentes.de.segurança..guardas..rondas.vigilantes.[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V73_PROFISSIONAIS_Educadores.Físicos=as.character(attributes.csv$V73_PROFISSIONAIS_Educadores.Físicos[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V74_PROFISSIONAIS_Assistentes.de.Recursos.Comunitários=as.character(attributes.csv$V74_PROFISSIONAIS_Assistentes.de.Recursos.Comunitários[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V75_PROFISSIONAIS_Auxiliares.de.almoxarifado=as.character(attributes.csv$V75_PROFISSIONAIS_Auxiliares.de.almoxarifado[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V76_PROFISSIONAIS_Educadores.Sociais=as.character(attributes.csv$V76_PROFISSIONAIS_Educadores.Sociais[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V77_PROFISSIONAIS_Pedagogos=as.character(attributes.csv$V77_PROFISSIONAIS_Pedagogos[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V78_PROFISSIONAIS_Auxiliares.administrativos=as.character(attributes.csv$V78_PROFISSIONAIS_Auxiliares.administrativos[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V79_PROFISSIONAIS_Recepcionistas=as.character(attributes.csv$V79_PROFISSIONAIS_Recepcionistas[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V80_PROFISSIONAIS_Serviços.gerais=as.character(attributes.csv$V80_PROFISSIONAIS_Serviços.gerais[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V81_PROFISSIONAIS_Cozinheiros=as.character(attributes.csv$V81_PROFISSIONAIS_Cozinheiros[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V82_PROFISSIONAIS_Motoristas=as.character(attributes.csv$V82_PROFISSIONAIS_Motoristas[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V83_PROFISSIONAIS_Porteiros=as.character(attributes.csv$V83_PROFISSIONAIS_Porteiros[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V84_PROFISSIONAIS_Outros=as.character(attributes.csv$V84_PROFISSIONAIS_Outros[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V85_PROFISSIONAIS_TOTAL_Profissionais=as.character(attributes.csv$V85_PROFISSIONAIS_TOTAL_Profissionais[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V86_PROFISSIONAIS_X1...Agentes.Comunitários.de.Saúde=as.character(attributes.csv$V86_PROFISSIONAIS_X1...Agentes.Comunitários.de.Saúde[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V87_PROFISSIONAIS_X2...Assistentes.Sociais=as.character(attributes.csv$V87_PROFISSIONAIS_X2...Assistentes.Sociais[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V88_PROFISSIONAIS_X3...Auxiliares.de.Enfermagem=as.character(attributes.csv$V88_PROFISSIONAIS_X3...Auxiliares.de.Enfermagem[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V89_PROFISSIONAIS_X4...Enfermeiros=as.character(attributes.csv$V89_PROFISSIONAIS_X4...Enfermeiros[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V90_PROFISSIONAIS_X5...Auxiliares.de.Consultório.Bucal=as.character(attributes.csv$V90_PROFISSIONAIS_X5...Auxiliares.de.Consultório.Bucal[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V91_PROFISSIONAIS_X6...Médicos=as.character(attributes.csv$V91_PROFISSIONAIS_X6...Médicos[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V92_PROFISSIONAIS_X7...Psicólogos=as.character(attributes.csv$V92_PROFISSIONAIS_X7...Psicólogos[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V93_PROFISSIONAIS_X8...Fisioterapeutas=as.character(attributes.csv$V93_PROFISSIONAIS_X8...Fisioterapeutas[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V94_PROFISSIONAIS_X9...Terapeutas.Ocupacionais=as.character(attributes.csv$V94_PROFISSIONAIS_X9...Terapeutas.Ocupacionais[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V95_PROFISSIONAIS_X10...Dentistas=as.character(attributes.csv$V95_PROFISSIONAIS_X10...Dentistas[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V96_PROFISSIONAIS_X11...Farmacêuticos=as.character(attributes.csv$V96_PROFISSIONAIS_X11...Farmacêuticos[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V97_PROFISSIONAIS_X12...Administradores=as.character(attributes.csv$V97_PROFISSIONAIS_X12...Administradores[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V98_PROFISSIONAIS_X13...Agentes.de.segurança..guardas..rondas.vigilantes.=as.character(attributes.csv$V98_PROFISSIONAIS_X13...Agentes.de.segurança..guardas..rondas.vigilantes.[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V99_PROFISSIONAIS_X14...Educadores.Físicos=as.character(attributes.csv$V99_PROFISSIONAIS_X14...Educadores.Físicos[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V100_PROFISSIONAIS_X15...Assistentes.de.Recursos.Comunitários=as.character(attributes.csv$V100_PROFISSIONAIS_X15...Assistentes.de.Recursos.Comunitários[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V101_PROFISSIONAIS_X16...Auxiliares.de.almoxarifado=as.character(attributes.csv$V101_PROFISSIONAIS_X16...Auxiliares.de.almoxarifado[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V102_PROFISSIONAIS_X17...Educadores.Sociais=as.character(attributes.csv$V102_PROFISSIONAIS_X17...Educadores.Sociais[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V103_PROFISSIONAIS_X18...Pedagogos=as.character(attributes.csv$V103_PROFISSIONAIS_X18...Pedagogos[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V104_PROFISSIONAIS_X19...Auxiliares.administrativos=as.character(attributes.csv$V104_PROFISSIONAIS_X19...Auxiliares.administrativos[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V105_PROFISSIONAIS_X20...Recepcionistas=as.character(attributes.csv$V105_PROFISSIONAIS_X20...Recepcionistas[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V106_PROFISSIONAIS_X21...Serviços.gerais=as.character(attributes.csv$V106_PROFISSIONAIS_X21...Serviços.gerais[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V107_PROFISSIONAIS_X22...Cozinheiros=as.character(attributes.csv$V107_PROFISSIONAIS_X22...Cozinheiros[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V108_PROFISSIONAIS_X23...Motoristas=as.character(attributes.csv$V108_PROFISSIONAIS_X23...Motoristas[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V109_PROFISSIONAIS_X24...Porteiros=as.character(attributes.csv$V109_PROFISSIONAIS_X24...Porteiros[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V110_PACIENTES_Média.atende.dia.típico.=as.character(attributes.csv$V110_PACIENTES_Média.atende.dia.típico.[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V111_PACIENTES_Média.capacidade.de.atender.=as.character(attributes.csv$V111_PACIENTES_Média.capacidade.de.atender.[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V112_PACIENTES_Porcentagem.tem.problemas.com.drogas..=as.character(attributes.csv$V112_PACIENTES_Porcentagem.tem.problemas.com.drogas..[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V113_PACIENTES_Porcentagem.tem.outros.problemas.de.saúde.mental..=as.character(attributes.csv$V113_PACIENTES_Porcentagem.tem.outros.problemas.de.saúde.mental..[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V114_RELACOES_UAPS.RURAL=as.character(attributes.csv$V114_RELACOES_UAPS.RURAL[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V115_RELACOES_UAPS.URBANA=as.character(attributes.csv$V115_RELACOES_UAPS.URBANA[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V116_RELACOES_Ajuda.Mútua=as.character(attributes.csv$V116_RELACOES_Ajuda.Mútua[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V117_RELACOES_Entidades.Assistênciais.e.Dependencia.Química.e.CT=as.character(attributes.csv$V117_RELACOES_Entidades.Assistênciais.e.Dependencia.Química.e.CT[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V118_RELACOES_Residência.Terapeutica=as.character(attributes.csv$V118_RELACOES_Residência.Terapeutica[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V119_RELACOES_Entidades.Socioassistenciais=as.character(attributes.csv$V119_RELACOES_Entidades.Socioassistenciais[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V120_RELACOES_Assistência.Hospitalar=as.character(attributes.csv$V120_RELACOES_Assistência.Hospitalar[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V121_RELACOES_CAPS=as.character(attributes.csv$V121_RELACOES_CAPS[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V122_RELACOES_CRAS=as.character(attributes.csv$V122_RELACOES_CRAS[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V123_RELACOES_CREAS=as.character(attributes.csv$V123_RELACOES_CREAS[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V124_RELACOES_Acolhimento.Institucional=as.character(attributes.csv$V124_RELACOES_Acolhimento.Institucional[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V125_RELACOES_Urgência.Emergência=as.character(attributes.csv$V125_RELACOES_Urgência.Emergência[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V126_RELACOES_Ambulatório.de.Saúde.Mental=as.character(attributes.csv$V126_RELACOES_Ambulatório.de.Saúde.Mental[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V127_RELACOES_Centro.de.Convivência=as.character(attributes.csv$V127_RELACOES_Centro.de.Convivência[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V128_RELACOES_Consultório.na.Rua=as.character(attributes.csv$V128_RELACOES_Consultório.na.Rua[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V129_RELACOES_OUTRO.SERVIÇO.NAO.LISTADO=as.character(attributes.csv$V129_RELACOES_OUTRO.SERVIÇO.NAO.LISTADO[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V130_RELACOES_NÚMERO.SERVIÇOS.NÃO.LISTADOS=as.character(attributes.csv$V130_RELACOES_NÚMERO.SERVIÇOS.NÃO.LISTADOS[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V131_GEO_kml_latitude=as.character(attributes.csv$V131_GEO_kml_latitude[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_with_zero)$V132_GEO_kml_longitude=as.character(attributes.csv$V132_GEO_kml_longitude[match(V(full_with_zero)$name, attributes.csv$V3_LABEL_ID2)])
```



```{r, message=FALSE, warning=FALSE, include=FALSE}
# The coolest part - adding attributes to each node (full_no_zero) - Update this code with "for" and after Pedro's updates regarding KML mercartor coordinates 
V(full_no_zero)$ID=as.character(attributes.csv$ID[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$TIPO1=as.character(attributes.csv$TIPO1[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$TIPO2=as.character(attributes.csv$TIPO2[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V1_LABEL_TIPO=as.character(attributes.csv$V1_LABEL_TIPO[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V2_LABEL_ID=as.character(attributes.csv$V2_LABEL_ID[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V3_LABEL_ID2=as.character(attributes.csv$V3_LABEL_ID2[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V4_LABEL_ID3=as.character(attributes.csv$V4_LABEL_ID3[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V5_LABEL_LABEL=as.character(attributes.csv$V5_LABEL_LABEL[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V6_COMUNICACAO_Dispõe.de.meios.de.comunicação=as.character(attributes.csv$V6_COMUNICACAO_Dispõe.de.meios.de.comunicação[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V7_COMUNICACAO_Telefeno.Fixo=as.character(attributes.csv$V7_COMUNICACAO_Telefeno.Fixo[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V8_COMUNICACAO_Celular.Chamada.de.Voz=as.character(attributes.csv$V8_COMUNICACAO_Celular.Chamada.de.Voz[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V9_COMUNICACAO_Celular.Mensagem.de.Texto=as.character(attributes.csv$V9_COMUNICACAO_Celular.Mensagem.de.Texto[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V10_COMUNICACAO_E.mail=as.character(attributes.csv$V10_COMUNICACAO_E.mail[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V11_COMUNICACAO_Skype.Menssager=as.character(attributes.csv$V11_COMUNICACAO_Skype.Menssager[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V12_COMUNICACAO_Converso.Pessalmente=as.character(attributes.csv$V12_COMUNICACAO_Converso.Pessalmente[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V13_COMUNICACAO_Comunicação.Institucional..Ofício..Memorando.=as.character(attributes.csv$V13_COMUNICACAO_Comunicação.Institucional..Ofício..Memorando.[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V14_COMUNICACAO_Outro=as.character(attributes.csv$V14_COMUNICACAO_Outro[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V15_COMUNICACAO_FACEBOOK.REDES.SOCAIS=as.character(attributes.csv$V15_COMUNICACAO_FACEBOOK.REDES.SOCAIS[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V16_TEMPO_FUNC_Data_Abertura=as.character(attributes.csv$V16_TEMPO_FUNC_Data_Abertura[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V17_TEMPO_FUNC_Data_Pesquisa=as.character(attributes.csv$V17_TEMPO_FUNC_Data_Pesquisa[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V18_TEMPO_FUNC_Idade_Serviço_Dias=as.character(attributes.csv$V18_TEMPO_FUNC_Idade_Serviço_Dias[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V19_TEMPO_FUNC_Idade_em_anos=as.character(attributes.csv$V19_TEMPO_FUNC_Idade_em_anos[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V20_FUNCIONAMENTO_Segunda=as.character(attributes.csv$V20_FUNCIONAMENTO_Segunda[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V21_FUNCIONAMENTO_Terça=as.character(attributes.csv$V21_FUNCIONAMENTO_Terça[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V22_FUNCIONAMENTO_Quarta=as.character(attributes.csv$V22_FUNCIONAMENTO_Quarta[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V23_FUNCIONAMENTO_Quinta=as.character(attributes.csv$V23_FUNCIONAMENTO_Quinta[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V24_FUNCIONAMENTO_Sexta=as.character(attributes.csv$V24_FUNCIONAMENTO_Sexta[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V25_FUNCIONAMENTO_Sábado=as.character(attributes.csv$V25_FUNCIONAMENTO_Sábado[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V26_FUNCIONAMENTO_Domingo=as.character(attributes.csv$V26_FUNCIONAMENTO_Domingo[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V27_FUNCIONAMENTO_Feriados=as.character(attributes.csv$V27_FUNCIONAMENTO_Feriados[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V28_FUNCIONAMENTO_Segunda....Manhã=as.character(attributes.csv$V28_FUNCIONAMENTO_Segunda....Manhã[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V29_FUNCIONAMENTO_Segunda....Tarde=as.character(attributes.csv$V29_FUNCIONAMENTO_Segunda....Tarde[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V30_FUNCIONAMENTO_Segunda....Noite=as.character(attributes.csv$V30_FUNCIONAMENTO_Segunda....Noite[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V31_FUNCIONAMENTO_Segunda....Plantão.24h=as.character(attributes.csv$V31_FUNCIONAMENTO_Segunda....Plantão.24h[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V32_FUNCIONAMENTO_Terça....Manhã=as.character(attributes.csv$V32_FUNCIONAMENTO_Terça....Manhã[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V33_FUNCIONAMENTO_Terça....Tarde=as.character(attributes.csv$V33_FUNCIONAMENTO_Terça....Tarde[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V34_FUNCIONAMENTO_Terça....Noite=as.character(attributes.csv$V34_FUNCIONAMENTO_Terça....Noite[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V35_FUNCIONAMENTO_Terça....Plantão.24h=as.character(attributes.csv$V35_FUNCIONAMENTO_Terça....Plantão.24h[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V36_FUNCIONAMENTO_Quarta....Manhã=as.character(attributes.csv$V36_FUNCIONAMENTO_Quarta....Manhã[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V37_FUNCIONAMENTO_Quarta....Tarde=as.character(attributes.csv$V37_FUNCIONAMENTO_Quarta....Tarde[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V38_FUNCIONAMENTO_Quarta....Noite=as.character(attributes.csv$V38_FUNCIONAMENTO_Quarta....Noite[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V39_FUNCIONAMENTO_Quarta....Plantão.24h=as.character(attributes.csv$V39_FUNCIONAMENTO_Quarta....Plantão.24h[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V40_FUNCIONAMENTO_Quinta....Manhã=as.character(attributes.csv$V40_FUNCIONAMENTO_Quinta....Manhã[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V41_FUNCIONAMENTO_Quinta....Tarde=as.character(attributes.csv$V41_FUNCIONAMENTO_Quinta....Tarde[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V42_FUNCIONAMENTO_Quinta....Noite=as.character(attributes.csv$V42_FUNCIONAMENTO_Quinta....Noite[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V43_FUNCIONAMENTO_Quinta....Plantão.24h=as.character(attributes.csv$V43_FUNCIONAMENTO_Quinta....Plantão.24h[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V44_FUNCIONAMENTO_Sexta....Manhã=as.character(attributes.csv$V44_FUNCIONAMENTO_Sexta....Manhã[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V45_FUNCIONAMENTO_Sexta....Tarde=as.character(attributes.csv$V45_FUNCIONAMENTO_Sexta....Tarde[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V46_FUNCIONAMENTO_Sexta....Noite=as.character(attributes.csv$V46_FUNCIONAMENTO_Sexta....Noite[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V47_FUNCIONAMENTO_Sexta....Plantão.24h=as.character(attributes.csv$V47_FUNCIONAMENTO_Sexta....Plantão.24h[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V48_FUNCIONAMENTO_Sábado....Manhã=as.character(attributes.csv$V48_FUNCIONAMENTO_Sábado....Manhã[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V49_FUNCIONAMENTO_Sábado....Tarde=as.character(attributes.csv$V49_FUNCIONAMENTO_Sábado....Tarde[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V50_FUNCIONAMENTO_Sábado....Noite=as.character(attributes.csv$V50_FUNCIONAMENTO_Sábado....Noite[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V51_FUNCIONAMENTO_Sábado....Plantão.24h=as.character(attributes.csv$V51_FUNCIONAMENTO_Sábado....Plantão.24h[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V52_FUNCIONAMENTO_Domingo....Manhã=as.character(attributes.csv$V52_FUNCIONAMENTO_Domingo....Manhã[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V53_FUNCIONAMENTO_Domingo....Tarde=as.character(attributes.csv$V53_FUNCIONAMENTO_Domingo....Tarde[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V54_FUNCIONAMENTO_Domingo....Noite=as.character(attributes.csv$V54_FUNCIONAMENTO_Domingo....Noite[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V55_FUNCIONAMENTO_Domingo....Plantão.24h=as.character(attributes.csv$V55_FUNCIONAMENTO_Domingo....Plantão.24h[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V56_FUNCIONAMENTO_Feriado....Manhã=as.character(attributes.csv$V56_FUNCIONAMENTO_Feriado....Manhã[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V57_FUNCIONAMENTO_Feriado....Tarde=as.character(attributes.csv$V57_FUNCIONAMENTO_Feriado....Tarde[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V58_FUNCIONAMENTO_Feriado....Noite=as.character(attributes.csv$V58_FUNCIONAMENTO_Feriado....Noite[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V59_FUNCIONAMENTO_Feriado....Plantão.24h=as.character(attributes.csv$V59_FUNCIONAMENTO_Feriado....Plantão.24h[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V60_PROFISSIONAIS_Agentes.Comunitários.de.Saúde=as.character(attributes.csv$V60_PROFISSIONAIS_Agentes.Comunitários.de.Saúde[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V61_PROFISSIONAIS_Assistentes.Sociais=as.character(attributes.csv$V61_PROFISSIONAIS_Assistentes.Sociais[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V62_PROFISSIONAIS_Auxiliares.de.Enfermagem=as.character(attributes.csv$V62_PROFISSIONAIS_Auxiliares.de.Enfermagem[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V63_PROFISSIONAIS_Enfermeiros=as.character(attributes.csv$V63_PROFISSIONAIS_Enfermeiros[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V64_PROFISSIONAIS_Auxiliares.de.Consultório.Bucal=as.character(attributes.csv$V64_PROFISSIONAIS_Auxiliares.de.Consultório.Bucal[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V65_PROFISSIONAIS_Médicos=as.character(attributes.csv$V65_PROFISSIONAIS_Médicos[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V66_PROFISSIONAIS_Psicólogos=as.character(attributes.csv$V66_PROFISSIONAIS_Psicólogos[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V67_PROFISSIONAIS_Fisioterapeutas=as.character(attributes.csv$V67_PROFISSIONAIS_Fisioterapeutas[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V68_PROFISSIONAIS_Terapeutas.Ocupacionais=as.character(attributes.csv$V68_PROFISSIONAIS_Terapeutas.Ocupacionais[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V69_PROFISSIONAIS_Dentistas=as.character(attributes.csv$V69_PROFISSIONAIS_Dentistas[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V70_PROFISSIONAIS_Farmacêuticos=as.character(attributes.csv$V70_PROFISSIONAIS_Farmacêuticos[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V71_PROFISSIONAIS_Administradores=as.character(attributes.csv$V71_PROFISSIONAIS_Administradores[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V72_PROFISSIONAIS_Agentes.de.segurança..guardas..rondas.vigilantes.=as.character(attributes.csv$V72_PROFISSIONAIS_Agentes.de.segurança..guardas..rondas.vigilantes.[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V73_PROFISSIONAIS_Educadores.Físicos=as.character(attributes.csv$V73_PROFISSIONAIS_Educadores.Físicos[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V74_PROFISSIONAIS_Assistentes.de.Recursos.Comunitários=as.character(attributes.csv$V74_PROFISSIONAIS_Assistentes.de.Recursos.Comunitários[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V75_PROFISSIONAIS_Auxiliares.de.almoxarifado=as.character(attributes.csv$V75_PROFISSIONAIS_Auxiliares.de.almoxarifado[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V76_PROFISSIONAIS_Educadores.Sociais=as.character(attributes.csv$V76_PROFISSIONAIS_Educadores.Sociais[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V77_PROFISSIONAIS_Pedagogos=as.character(attributes.csv$V77_PROFISSIONAIS_Pedagogos[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V78_PROFISSIONAIS_Auxiliares.administrativos=as.character(attributes.csv$V78_PROFISSIONAIS_Auxiliares.administrativos[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V79_PROFISSIONAIS_Recepcionistas=as.character(attributes.csv$V79_PROFISSIONAIS_Recepcionistas[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V80_PROFISSIONAIS_Serviços.gerais=as.character(attributes.csv$V80_PROFISSIONAIS_Serviços.gerais[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V81_PROFISSIONAIS_Cozinheiros=as.character(attributes.csv$V81_PROFISSIONAIS_Cozinheiros[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V82_PROFISSIONAIS_Motoristas=as.character(attributes.csv$V82_PROFISSIONAIS_Motoristas[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V83_PROFISSIONAIS_Porteiros=as.character(attributes.csv$V83_PROFISSIONAIS_Porteiros[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V84_PROFISSIONAIS_Outros=as.character(attributes.csv$V84_PROFISSIONAIS_Outros[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V85_PROFISSIONAIS_TOTAL_Profissionais=as.character(attributes.csv$V85_PROFISSIONAIS_TOTAL_Profissionais[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V86_PROFISSIONAIS_X1...Agentes.Comunitários.de.Saúde=as.character(attributes.csv$V86_PROFISSIONAIS_X1...Agentes.Comunitários.de.Saúde[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V87_PROFISSIONAIS_X2...Assistentes.Sociais=as.character(attributes.csv$V87_PROFISSIONAIS_X2...Assistentes.Sociais[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V88_PROFISSIONAIS_X3...Auxiliares.de.Enfermagem=as.character(attributes.csv$V88_PROFISSIONAIS_X3...Auxiliares.de.Enfermagem[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V89_PROFISSIONAIS_X4...Enfermeiros=as.character(attributes.csv$V89_PROFISSIONAIS_X4...Enfermeiros[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V90_PROFISSIONAIS_X5...Auxiliares.de.Consultório.Bucal=as.character(attributes.csv$V90_PROFISSIONAIS_X5...Auxiliares.de.Consultório.Bucal[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V91_PROFISSIONAIS_X6...Médicos=as.character(attributes.csv$V91_PROFISSIONAIS_X6...Médicos[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V92_PROFISSIONAIS_X7...Psicólogos=as.character(attributes.csv$V92_PROFISSIONAIS_X7...Psicólogos[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V93_PROFISSIONAIS_X8...Fisioterapeutas=as.character(attributes.csv$V93_PROFISSIONAIS_X8...Fisioterapeutas[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V94_PROFISSIONAIS_X9...Terapeutas.Ocupacionais=as.character(attributes.csv$V94_PROFISSIONAIS_X9...Terapeutas.Ocupacionais[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V95_PROFISSIONAIS_X10...Dentistas=as.character(attributes.csv$V95_PROFISSIONAIS_X10...Dentistas[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V96_PROFISSIONAIS_X11...Farmacêuticos=as.character(attributes.csv$V96_PROFISSIONAIS_X11...Farmacêuticos[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V97_PROFISSIONAIS_X12...Administradores=as.character(attributes.csv$V97_PROFISSIONAIS_X12...Administradores[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V98_PROFISSIONAIS_X13...Agentes.de.segurança..guardas..rondas.vigilantes.=as.character(attributes.csv$V98_PROFISSIONAIS_X13...Agentes.de.segurança..guardas..rondas.vigilantes.[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V99_PROFISSIONAIS_X14...Educadores.Físicos=as.character(attributes.csv$V99_PROFISSIONAIS_X14...Educadores.Físicos[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V100_PROFISSIONAIS_X15...Assistentes.de.Recursos.Comunitários=as.character(attributes.csv$V100_PROFISSIONAIS_X15...Assistentes.de.Recursos.Comunitários[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V101_PROFISSIONAIS_X16...Auxiliares.de.almoxarifado=as.character(attributes.csv$V101_PROFISSIONAIS_X16...Auxiliares.de.almoxarifado[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V102_PROFISSIONAIS_X17...Educadores.Sociais=as.character(attributes.csv$V102_PROFISSIONAIS_X17...Educadores.Sociais[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V103_PROFISSIONAIS_X18...Pedagogos=as.character(attributes.csv$V103_PROFISSIONAIS_X18...Pedagogos[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V104_PROFISSIONAIS_X19...Auxiliares.administrativos=as.character(attributes.csv$V104_PROFISSIONAIS_X19...Auxiliares.administrativos[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V105_PROFISSIONAIS_X20...Recepcionistas=as.character(attributes.csv$V105_PROFISSIONAIS_X20...Recepcionistas[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V106_PROFISSIONAIS_X21...Serviços.gerais=as.character(attributes.csv$V106_PROFISSIONAIS_X21...Serviços.gerais[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V107_PROFISSIONAIS_X22...Cozinheiros=as.character(attributes.csv$V107_PROFISSIONAIS_X22...Cozinheiros[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V108_PROFISSIONAIS_X23...Motoristas=as.character(attributes.csv$V108_PROFISSIONAIS_X23...Motoristas[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V109_PROFISSIONAIS_X24...Porteiros=as.character(attributes.csv$V109_PROFISSIONAIS_X24...Porteiros[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V110_PACIENTES_Média.atende.dia.típico.=as.character(attributes.csv$V110_PACIENTES_Média.atende.dia.típico.[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V111_PACIENTES_Média.capacidade.de.atender.=as.character(attributes.csv$V111_PACIENTES_Média.capacidade.de.atender.[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V112_PACIENTES_Porcentagem.tem.problemas.com.drogas..=as.character(attributes.csv$V112_PACIENTES_Porcentagem.tem.problemas.com.drogas..[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V113_PACIENTES_Porcentagem.tem.outros.problemas.de.saúde.mental..=as.character(attributes.csv$V113_PACIENTES_Porcentagem.tem.outros.problemas.de.saúde.mental..[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V114_RELACOES_UAPS.RURAL=as.character(attributes.csv$V114_RELACOES_UAPS.RURAL[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V115_RELACOES_UAPS.URBANA=as.character(attributes.csv$V115_RELACOES_UAPS.URBANA[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V116_RELACOES_Ajuda.Mútua=as.character(attributes.csv$V116_RELACOES_Ajuda.Mútua[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V117_RELACOES_Entidades.Assistênciais.e.Dependencia.Química.e.CT=as.character(attributes.csv$V117_RELACOES_Entidades.Assistênciais.e.Dependencia.Química.e.CT[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V118_RELACOES_Residência.Terapeutica=as.character(attributes.csv$V118_RELACOES_Residência.Terapeutica[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V119_RELACOES_Entidades.Socioassistenciais=as.character(attributes.csv$V119_RELACOES_Entidades.Socioassistenciais[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V120_RELACOES_Assistência.Hospitalar=as.character(attributes.csv$V120_RELACOES_Assistência.Hospitalar[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V121_RELACOES_CAPS=as.character(attributes.csv$V121_RELACOES_CAPS[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V122_RELACOES_CRAS=as.character(attributes.csv$V122_RELACOES_CRAS[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V123_RELACOES_CREAS=as.character(attributes.csv$V123_RELACOES_CREAS[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V124_RELACOES_Acolhimento.Institucional=as.character(attributes.csv$V124_RELACOES_Acolhimento.Institucional[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V125_RELACOES_Urgência.Emergência=as.character(attributes.csv$V125_RELACOES_Urgência.Emergência[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V126_RELACOES_Ambulatório.de.Saúde.Mental=as.character(attributes.csv$V126_RELACOES_Ambulatório.de.Saúde.Mental[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V127_RELACOES_Centro.de.Convivência=as.character(attributes.csv$V127_RELACOES_Centro.de.Convivência[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V128_RELACOES_Consultório.na.Rua=as.character(attributes.csv$V128_RELACOES_Consultório.na.Rua[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V129_RELACOES_OUTRO.SERVIÇO.NAO.LISTADO=as.character(attributes.csv$V129_RELACOES_OUTRO.SERVIÇO.NAO.LISTADO[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V130_RELACOES_NÚMERO.SERVIÇOS.NÃO.LISTADOS=as.character(attributes.csv$V130_RELACOES_NÚMERO.SERVIÇOS.NÃO.LISTADOS[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V131_GEO_kml_latitude=as.character(attributes.csv$V131_GEO_kml_latitude[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
V(full_no_zero)$V132_GEO_kml_longitude=as.character(attributes.csv$V132_GEO_kml_longitude[match(V(full_no_zero)$name, attributes.csv$V3_LABEL_ID2)])
```

#Basic Proof 
```{r, message=FALSE, warning=FALSE, include=FALSE}
#The most important test full_no_zero
a=get.vertex.attribute(full_no_zero, 'V2_LABEL_ID')
b=attributes.csv$V3_LABEL_ID2
c=cbind(a,b)
head(c)

#The most important test full_no_zero
d=get.vertex.attribute(full_with_zero, 'V2_LABEL_ID')
b=attributes.csv$V3_LABEL_ID2
e=cbind(d,b)
head(e)
```

#Exporting to Photoshop...Ops Gephi
```{r, message=FALSE, warning=FALSE, include=FALSE}
saveAsGEXF(full_no_zero, "~/Banco Redes R/full_no_zero.gexf")
saveAsGEXF(full_no_zero, "~/Banco Redes R/full_with_zero.gexf")
```


```{r}
krack_reports_to_only <- delete.edges(full, 
                                      E(full)[get.edge.attribute(full, 
                                                                       name = "var1") == 0])
plot(krack_reports_to_only)

reports_to_layout <- layout.fruchterman.reingold(krack_reports_to_only)

plot(reports_to_layout)

reports_to_layout <- layout.fruchterman.reingold(krack_reports_to_only)
pdf("1.5_Krackhardt_Reports_Fruchterman_Reingold.pdf")
plot(krack_reports_to_only, 
     layout=reports_to_layout)
dev.off()


tenure_vertex_sizes = get.vertex.attribute(full,"total")

pdf("1.7_Krackhardt_Reports_Vertex_Size.pdf") 
plot(krack_reports_to_only, 
     layout=reports_to_layout, 
     vertex.label=NA, 
     edge.arrow.size=.5,
     vertex.size=tenure_vertex_sizes)
dev.off() 




write.graph(full, file='krack_full.txt', format="edgelist")
```

```{r}
###
# 4. VISUALIZE THE NETWORKS
###
 
# We can use R's general-purpose plot() method to generate custom
# visualizations of the network.

# R only lets us look at one plot at a time.  To make our work easier
# we will save our plots as PDF files.  To jus create a plot execute 
# the code between the PDF function and "dev.off()".

# In order to save PDF files we must tell R where to put them.  We do
# this with the setwd() command.  You must put the full path to the
# folder where you will output the files here.

# In OS X you can get this information by selecting the folder, right
# clicking and selecting "Get Info."  The path is listed under "Where."

# In Windows you can get this information by selecting the folder, right
# clicking and selecting "Properties."  The path information is listed 
# "location".

# example: setwd("/Users/seanwestwood/Desktop/lab_1")
setwd("~/Banco Redes R/Grafos")
  
# First, let's plot the network with all possible ties.
pdf("full_no_zero.pdf")
plot(full_no_zero)
dev.off()
 
# This is a bit of a jumble, so let's look at the networks for
# single edge types.
 
# Total
full_total_only <- delete.edges(full_no_zero, 
    E(full_no_zero)[get.edge.attribute(full_no_zero,
    name = "total") == 0])
summary(full_total_only)
pdf("full_no_zero_total.pdf")
plot(full_total_only)
dev.off()

# Still kind of messy, so let's clean things up a bit. For 
# simplicity, we'll focus on reports_to ties for now.
 
# First, we can optimize the layout by applying the layout 
# algorithm to the specific set of ties we care about. Here 
# we'll use Fruchterman-Rheingold; other options are 
# described in the igraph help page for "layout," which 
# can be accessed by entering ?layout.

total_to_layout <- layout.fruchterman.reingold(full_total)
pdf("full_no_zero_total_layout.pdf")
plot(full_total_only, 
     layout=total_to_layout)
dev.off()
 
# Now let's color-code vertices by department and clean up the 
# plot by removing vertex labels and shrinking the arrow size. 
TIPO1_label = get.vertex.attribute(full_total,"V1_LABEL_TIPO")

TIPO1_vertex_colors = get.vertex.attribute(full_total,"V1_LABEL_TIPO")
sort(table(V(full_total)$V1_LABEL_TIPO))
colors = c('Black', 'Red', 'Blue', 'Yellow', 'Green')
TIPO1_vertex_colors[TIPO1_vertex_colors == "UAPS-URBANA"] = colors[1]
TIPO1_vertex_colors[TIPO1_vertex_colors == "Ajuda Mútua"] = colors[2]
TIPO1_vertex_colors[TIPO1_vertex_colors == "UAPS-RURAL"] = colors[3]
TIPO1_vertex_colors[TIPO1_vertex_colors == "Entidades Assistênciais e Dependencia Química e CT"] = colors[4] 
TIPO1_vertex_colors[TIPO1_vertex_colors == "Residência Terapeutica"] = colors[5]
TIPO1_vertex_colors[TIPO1_vertex_colors == "Ambulatório de Saúde Mental"] = colors[5] 
TIPO1_vertex_colors[TIPO1_vertex_colors == "Centro de Convivência"] = colors[5] 
TIPO1_vertex_colors[TIPO1_vertex_colors == "Território Aliança pela Vida"] = colors[1] 
TIPO1_vertex_colors[TIPO1_vertex_colors == "Urgência/Emergência"] = colors[5]
TIPO1_vertex_colors[TIPO1_vertex_colors == "Consultório na Rua"] = colors[5]
TIPO1_vertex_colors[TIPO1_vertex_colors == "Acolhimento Institucional"] = colors[5] 
TIPO1_vertex_colors[TIPO1_vertex_colors == "CREAS"] = colors[2]
TIPO1_vertex_colors[TIPO1_vertex_colors == "CAPS"] = colors[5]
TIPO1_vertex_colors[TIPO1_vertex_colors == "Assistência Hospitalar"] = colors[5] 
TIPO1_vertex_colors[TIPO1_vertex_colors == "CRAS"] = colors[5]
TIPO1_vertex_colors[TIPO1_vertex_colors == "Entidades Socioassistenciais"] = colors[5] 



pdf("full_no_zero_color.pdf") 
plot(full_total_only, 
    layout=reports_to_layout, 
    vertex.color=TIPO1_vertex_colors, 
    vertex.label=NA, 
    edge.arrow.size=.5)
dev.off() 

# Now let's set the vertex size by total.
total_vertex_sizes = get.vertex.attribute(full_no_zero,"V85_PROFISSIONAIS_TOTAL_Profissionais")
total_vertex_sizes = as.character(total_vertex_sizes)
total_vertex_sizes = as.numeric(total_vertex_sizes)

pdf("full_no_zero_vertex_size.pdf") 
plot(full_total_only, 
     layout=reports_to_layout, 
     vertex.color=TIPO1_vertex_colors, 
     vertex.label=NA, 
     edge.arrow.size=.5,
     vertex.size=(total_vertex_sizes)/5)
dev.off() 
 
# Now let's incorporate additional tie types. We'll use the 
# layout generated by the reports-to ties but overlay the 
# advice and friendship ties in red and blue.

tie_type_colors = c(rgb(1,0,0,.5), rgb(0,0,1,.5), rgb(0,0,0,.5))
E(full_no_zero)$color[ E(full_no_zero)$atividade==1 ] = tie_type_colors[1]
E(full_no_zero)$color[ E(full_no_zero)$acesso==1 ] = tie_type_colors[2]
E(full_no_zero)$color[ E(full_no_zero)$confianca==1 ] = tie_type_colors[3]
E(full_no_zero)$arrow.size=.5 
V(full_no_zero)$color = TIPO1_vertex_colors
V(full_no_zero)$frame = TIPO1_vertex_colors

pdf("full_no_zero_tie_overlay.pdf")
plot(full_no_zero, 
     layout=reports_to_layout, 
     vertex.color=TIPO1_vertex_colors, 
     vertex.label=NA, 
     edge.arrow.size=.1,
     vertex.size=(total_vertex_sizes)/5)
 
 
# Add a legend. Note that the plot window must be open for this to 
# work.
legend(1, 
       1.25,
       legend = c('atividade', 
                  'acesso',
                  'confianca'), 
       col = tie_type_colors, 
       lty=1,
       cex = .3)
dev.off() 
 
# Another option for visualizing different network ties relative 
# to one another is to overlay the edges from one tie type on the 
# structure generated by another tie type. Here we can use the
# reports-to layout but show the friendship ties:

pdf("full_no_zero_overlayed_structure.pdf")
plot(full_total_only, 
     layout=reports_to_layout, 
     vertex.color=TIPO1_vertex_colors, 
     vertex.label=NA, 
     edge.arrow.size=.5,
     vertex.size=(total_vertex_sizes)/5, 
     main='Testing Pre-Historical Gephi')
dev.off() 
 
 
###
# 5. EXPORT THE NETWORK
###
 
setwd("~/Banco Redes R")
# The write.graph() function exports a graph object in various
# formats readable by other programs. There is no explicit
# option for a UCINET data type, but you can export the graph
# as a Pajek object by setting the 'format' parameter to 'pajek.'
# Note that the file will appear in whichever directory is set 
# as the default in R's preferences, unless you previously 
# changed this via setwd().
write.graph(full_no_zero, file='full_no_zero.dl', format="pajek")
 
# For a more general file type (e.g., importable to Excel),
# use the "edgelist" format. Note that neither of these will
# write the attributes; only the ties are maintained.
write.graph(full_no_zero, file='full_no_zero.txt', format="edgelist")
```
