---
title: "SNA Heterogeneity fuull_no_zero_fancy"
author: "Leonardo Martins"
date: "17 de julho de 2016"
output: 
  html_document: 
    fig_caption: yes
    fig_height: 12
    fig_width: 12
    keep_md: yes
    number_sections: yes
    theme: flatly
    toc: yes
---
SNA Descritive Analysis from "Projeto Redes de Atenção às pessoas que consomem álcool e outras Drogas em Juiz de Fora-MG   Brazil"  - SNArRDJF

Here you can find a basic script to analysis data from SNArRDJF - this script was elaborated considering its use for orther matrix adjacency data from SNArRDJF - Here we are going to analyse:

# fuull_no_zero_fancy

`#########################
`# Basic Preparation #####
`#########################

#Loading objects generated with previous script 
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
rm(list = ls()) # removing previous objects to be sure that we don't have objects conflicts name
load("~/SNArRDJF/Robject/15_diameter_full_no_zero.RData")
```
##Reload packages
```{r, message=TRUE, warning=TRUE}
suppressMessages(library(RColorBrewer))
suppressMessages(library(car))
suppressMessages(library(xtable))
suppressMessages(library(igraph))
suppressMessages(library(miniCRAN))
suppressMessages(library(magrittr))
suppressMessages(library(keyplayer))
suppressMessages(library(dplyr))
suppressMessages(library(feather))
suppressMessages(library(visNetwork))
suppressMessages(library(knitr))
suppressMessages(library(DT))
```
##Adding phantom tools
```{r, message=TRUE, warning=TRUE}
#In order to get dinamic javascript object install those ones. If you get problems installing go to Stackoverflow.com and type your error to discover what to do. In some cases the libraries need to be intalled in outside R libs.
#devtools::install_github("wch/webshot")
#webshot::install_phantomjs()
```
##Setting a random seed - this is a good strategy to keep the same graph pattern layout in a new report generation
```{r, message=TRUE, warning=TRUE}
set.seed(123)
```

##Simplify Graph - removing loops and duble edges 
```{r, echo=T, message=FALSE, warning=FALSE}
full_no_zero<-simplify(full_no_zero) #Simplify
```

```{r}

### 
# 4. HETEROGENEITY 
###

# Miller and McPherson write about processes of homophily and
# here we take a brief look at one version of this issue. 
# In particular, we look at the extent to which each actor's
# "associates" (friend, advisor, boos) are heterogenous or not.

# We'll use a statistic called the IQV, or Index of Qualitative
# Variation. This is just an implementation of Blau's Index of
# Heterogeneity (known to economists as the Herfindahl-Hirschman
# index), normalized so that perfect heterogeneity (i.e., equal 
# distribution across categories) equals 1.

# NOTE that this code only works with categorical variables that 
# have been numerically coded to integer values that ascend
# sequentially from 0; you may have to recode your data to get this
# to work properly.
# We are interested in many of the attributes of nodes.  To save 
# time and to make our lives better we are going to create a function
# that will provide an IQV statistic for any network and for
# any categorical variable.  A function is a simple way to
# create code that is both reusable and easier to edit.

# Functions have names and receive arguments.  For example,
# anytime you call table() you are calling the table function.
# We could write code to duplicate the table function for each
# of our variables, but it is faster to write a single general tool
# that will provide frequencies for any variable. If I have
# a dataframe with the variable gender and I want to see the
# split of males and females I would pass the argument
# "dataframe$gender" to the table function. We follow a
# similar model here. Understanding each step is less important
# than understanding the usefulness and power of functions.

get_iqvs <- function(graph, attribute) {

#we have now defined a function, get_iqvs, that will take the
# graph "graph" and find the iqv statistic for the categorical
# variable "attribute." Within this function whenever we use the 
#variables graph or attribute they correspond to the graph and
# variable we passed (provided) to the function

mat <- get.adjacency(graph)
				
# To make this function work on a wide variety of variables we
# find out how many coded levels (unique responses) exist for
# the attribute variable programatically

	attr_levels = get.vertex.attribute(graph,
	                                   attribute,
	                                   V(graph))
	
	num_levels = length(unique(attr_levels))
	iqvs = rep(0, nrow(mat))

# Now that we know how many levels exist we want to loop
# (go through) each actor in the network. Loops iterate through
# each value in a range.  Here we are looking through each ego
# in the range of egos starting at the first and ending at the
# last.  The function nrow provides the number of rows in an
# object and the ":" opperand specifies the range.  Between
# the curly braces of the for loop ego will represent exactly
# one value between 1 and the number of rows in the graph
# object, iterating by one during each execution of the loop.

	for (ego in 1:nrow(mat)) {
		
		# initialize actor-specific variables
		alter_attr_counts = rep(0, num_levels)
		num_alters_this_ego = 0
		sq_fraction_sum = 0

# For each ego we want to check each tied alter for the same
# level on the variable attribute as the ego.
	
		for (alter in 1:ncol(mat)) {
			
			# only examine alters that are actually tied to ego
			if (mat[ego, alter] == 1) {
				
				num_alters_this_ego = num_alters_this_ego + 1

				# get the alter's level on the attribute 
				alter_attr = get.vertex.attribute(graph, 
				    attribute, (alter - 1))

				# increment the count of alters with this level
				# of the attribute by 1
				alter_attr_counts[alter_attr + 1] =
				    alter_attr_counts[alter_attr + 1] + 1
			}
		}

		# now that we're done looping through all of the alters,
		# get the squared fraction for each level of the attribute
		# out of the total number of attributes
		for (i in 1:num_levels) {
			attr_fraction = alter_attr_counts[i] /
			    num_alters_this_ego
			sq_fraction_sum = sq_fraction_sum + attr_fraction ^ 2
		}
		
		# now we can compute the ego's blau index...
		blau_index = 1 - sq_fraction_sum
		
		# and the ego's IQV, which is just a normalized blau index
		iqvs[ego] = blau_index / (1 - (1 / num_levels))
	}

# The final part of a function returns the calculated value.
#  So if we called get_iqvs(testgraph, gender) return would
# provide the iqvs for gender in the test graph.  If we are also
# intersted in race we could simply change the function call
# to get_iqvs(testgraph, race).  No need to write all this
# code again for different variables.

	return(iqvs)
}



# For this data set, we'll look at homophily across departments, 
# which is already coded 0-4, so no recoding is needed. 
```

#Preparing Categorical Variabel as Numeric starting with zero 
```{r}
V(full_no_zero)$TIPO1_NUMERIC<-V(full_no_zero)$TIPO1
V(full_no_zero)$TIPO1_NUMERIC[V(full_no_zero)$TIPO1_NUMERIC=="Público"]<-0
V(full_no_zero)$TIPO1_NUMERIC[V(full_no_zero)$TIPO1_NUMERIC=="Privado"]<-1

V(full_no_zero)$TIPO1_NUMERIC_iqv<-as.numeric(get.vertex.attribute(full_no_zero,"TIPO1_NUMERIC"))
```

```{r}
V(full_no_zero)$tipo_iqv<-get_iqvs(full_no_zero, 'TIPO1_NUMERIC_iqv')
table<-cbind(V(full_no_zero)$tipo_iqv, V(full_no_zero)$TIPO1,
V(full_no_zero)$LABEL_COR)

datatable(table)
tipo_iqv_table<-get.vertex.attribute(full_no_zero, 'tipo_iqv') 
TIPO1_table<-get.vertex.attribute(full_no_zero, 'TIPO1')
LABEL_COR_table<-get.vertex.attribute(full_no_zero, 'LABEL_COR')
table<-cbind(LABEL_COR_table, TIPO1_table,tipo_iqv_table)
datatable(table)
```

#Saving objects with new variables and changes
```{r, echo=T, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
save.image("~/SNArRDJF/Robject/16_heteregeneity_full_no_zero.RData") 
```
